---
title: "01_Cleaning"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide  
---


```{r setup}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)

# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#importing functions
#source("functions.r")
``` 

# Introduction 

This script contains the code used to clean the raw datasets accessed from the NLSY97 contained within the `/RawData` directory. All datasets generated from this script will be saved in the `/CleanData` directory. 

A description of variables and project overview may be found in the project README. 
A data dictionary containing details about variables created may be accessed in the file `/CleanData/DataDictionary.xlsx`.

Functions used to clean the datasets may be accessed from the `/Scripts/functions.R` file.   

# ALCUSE Data 

`"ALCUSE.dat"` contains descriptive variables about alcohol use. `R1235800` (Primary CV Sample Type), `S0922200` (Drank Since Last Interview 2002), `S0922300` (# Days drinking alcohol in last 30 days 2002), `S0922400` (# Drinks per day in last 30 days 2002), and `S0922600`(# Days drinking alcohol during school week 2002). None of these variables are intended to be in our models, but they may be useful for descriptive statistics.  

We will clean up these variables, applying formats and renaming them for ease of future use.  

```{r alcuse}
alcuse <-  read.table('../RawData/ALCUSE.dat', sep=' ')
names(alcuse)<- c('id',
  'cv_samp',
  'drank_since_interview_02',
  'num_days_drink_02',
  'num_drinks_p_day_02',
  'num_days_drink_p_school_week') 
head(alcuse) 
dim(alcuse)
```  

# R6_2 Data 

This dataset contains a whole bunch of variables, many of which we do not need. We are only going to focus on retaining the variables pertaining to our study.



