---
title: "01_Cleaning"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide  
---


```{r setup}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)

# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#importing functions
#source("functions.r")
``` 

# Introduction 

This script contains the code used to clean the raw datasets accessed from the NLSY97 contained within the `/RawData` directory. All datasets generated from this script will be saved in the `/CleanData` directory. 

A description of variables and project overview may be found in the project README. 
A data dictionary containing details about variables created may be accessed in the file `/CleanData/DataDictionary.xlsx`.

Functions used to clean the datasets may be accessed from the `/Scripts/functions.R` file.   

# ALCUSE Data 

`"ALCUSE.dat"` contains descriptive variables about alcohol use. `R1235800` (Primary CV Sample Type), `S0922200` (Drank Since Last Interview 2002), `S0922300` (# Days drinking alcohol in last 30 days 2002), `S0922400` (# Drinks per day in last 30 days 2002), and `S0922600`(# Days drinking alcohol during school week 2002). None of these variables are intended to be in our models, but they may be useful for descriptive statistics.  

We will clean up these variables, applying formats and renaming them for ease of future use.  

```{r alcuse}
new_data <-  read.table('../RawData/ALCUSE.dat', sep=' ') 
names(new_data) <- c('R0000100', #Id
  'R1235800', #Cv samp
  'S0922200', #Drank since interview 02
  'S0922300', #Days drinking alc in last 30 
  'S0922400', #Num drinks per day
  'S0922600') #Num days drinking alc during school week

# Handle missing values

new_data[new_data == -1] = NA  # Refused
new_data[new_data == -2] = NA  # Dont know
new_data[new_data == -3] = NA  # Invalid missing
new_data[new_data == -4] = NA  # Valid missing
new_data[new_data == -5] = NA  # Non-interview

#Factor variables 

#CV Sample
new_data$R1235800 <- factor(new_data$R1235800,
    levels=c(0.0,1.0),
    labels=c("Oversample",
      "Cross-sectional")
  )

#Drank since last interview
new_data$S0922200 <- factor(new_data$S0922200,
    levels=c(0.0,1.0),
    labels=c("NO",
      "YES")
  )

#Num drinks per day in last 30 days  
range(new_data$S0922400, na.rm=TRUE) 
  #we have the option to change this into a factor variable, but this is probably better as a numeric descriptive stat.

```   

There are two variables that are factor variables according to the NLSY97 data dictionary and codes provided, but these variables are stored numerically, and there is not a whole lot of use in making them into categories. Below is the code to change them into factor variables, if we end up deciding to use them. 

```{r alcuse_factor_variables, eval = FALSE}  
#Factor option for Number of drinks per day
new_data$S0922400 <- factor(new_data$S0922400,
    levels=c(0.0,1.0,2.0,3.0,4.0,5.0,6.0,7.0,8.0,9.0,10.0,11.0,12.0,13.0,14.0,15.0),
    labels=c("0",
      "1",
      "2",
      "3",
      "4",
      "5",
      "6",
      "7",
      "8",
      "9",
      "10",
      "11",
      "12",
      "13",
      "14",
      "15+")
  ) 

#Factor option for number of days drinking alc during school week 
new_data <- new_data %>%
  mutate(
    S0922600 = case_when(
      between(S0922600, 1, 4)   ~ 1,
      between(S0922600, 5, 9)   ~ 5,
      between(S0922600, 10, 14) ~ 10,
      between(S0922600, 15, 19) ~ 15,
      between(S0922600, 20, 24) ~ 20,
      between(S0922600, 25, 29) ~ 25,
      TRUE ~ S0922600
    )
  )

  new_data$S0922600 <- factor(new_data$S0922600,
    levels=c(0.0,1.0,5.0,10.0,15.0,20.0,25.0,30.0),
    labels=c("0",
      "1 TO 4",
      "5 TO 9",
      "10 TO 14",
      "15 TO 19",
      "20 TO 24",
      "25 TO 29",
      "30")
  )

  #Factor option for number days drinking 
 new_data <- new_data %>%
  mutate(
    S0922300 = case_when(
      between(S0922300, 1, 4)   ~ 1,
      between(S0922300, 5, 9)   ~ 5,
      between(S0922300, 10, 14) ~ 10,
      between(S0922300, 15, 19) ~ 15,
      between(S0922300, 20, 24) ~ 20,
      between(S0922300, 25, 29) ~ 25,
      TRUE ~ S0922300
    )
  ) 
new_data$S0922300 <- factor(new_data$S0922300,
    levels=c(0.0,1.0,5.0,10.0,15.0,20.0,25.0,30.0),
    labels=c("0",
      "1 TO 4",
      "5 TO 9",
      "10 TO 14",
      "15 TO 19",
      "20 TO 24",
      "25 TO 29",
      "30")
  )

```
 
 
Lastly, we will rename our variable names with clearer naming conventions and save to a dataset called "alcuse" that we can then use when we merge our datasets. 

```{r renaming_alcuse_variables}
alcuse <- new_data
names(alcuse)<- c('id',
  'cv_samp',
  'drank_since_interview_02',
  'num_days_drink_02',
  'num_drinks_p_day_02',
  'num_days_drink_p_school_week') 
head(alcuse)
glimpse(alcuse)
```
 
# R6_2 Data 

This dataset contains a whole bunch of variables, many of which we do not need. We are only going to focus on retaining the variables pertaining to our study (there are some others included that I suspect may be useful descriptors or confounders).

```{r r6_2_dat} 
#variables we want 
vars_R6 <- c('R0000100', #id
          'R0536300', #sex
          'R0536401', #bdate month
          'R0536402', #bdate year
          'R0538600', #ethnicity
          'R0538700', #race
          'R1204500', #annual income, 97
          'R1485700', #mom's monitor, 97
          'R1485800', #dad's monitor, 97
          'R1486500', #mom's parent style, 97
          'R1486600', #dad's parent style, 97
          'R1487000', #fam/home risk index 97
          'R1487100', #physical environment risk index 97
          'R1487800', #substance use index 1997
          'S0921800', # Num cigs smoked/day last 30 days
          'S0923900',#Age 1st time use oth drugs 2002
          'R1482600')  #Race_ethnicity combined

new_data <- read.table('../RawData/R6_2.dat', sep=' ')
names(new_data) <- c('R0000100',
  'R0536300',
  'R0536401',
  'R0536402',
  'R0538600',
  'R0538700',
  'R1201300',
  'R1204500',
  'R1204700',
  'R1204900',
  'R1235800',
  'R1302400',
  'R1302500',
  'R1302600',
  'R1302700',
  'R1482600',
  'R1485700',
  'R1485800',
  'R1485900',
  'R1486000',
  'R1486100',
  'R1486200',
  'R1486300',
  'R1486400',
  'R1486500',
  'R1486600',
  'R1486700',
  'R1486800',
  'R1486900',
  'R1487000',
  'R1487100',
  'R1487200',
  'R1487300',
  'R1487400',
  'R1487500',
  'R1487600',
  'R1487700',
  'R1487800',
  'S0201500',
  'S0202000',
  'S0921600',
  'S0921700',
  'S0921800',
  'S0923700',
  'S0923900',
  'S0924000',
  'S0924100',
  'S0924200',
  'S1055500',
  'S1055600',
  'S1055800',
  'S1055900',
  'S1057000',
  'S1057100',
  'S1225600',
  'S1225700',
  'S1225800',
  'S1240700',
  'S1240800',
  'S1240801',
  'S1240802',
  'S1240803',
  'S1240804',
  'S1240805',
  'S1242800',
  'S1243100',
  'S1243200',
  'S1243201',
  'S1243202',
  'S1243203',
  'S1243204',
  'S1243205',
  'S1243206',
  'S1243207',
  'S1246500',
  'S1246600',
  'S1246601',
  'S1246602',
  'S1246603',
  'S1249300',
  'S1249400',
  'S1249401',
  'S1249402',
  'S1249600',
  'S1249900',
  'S1250100',
  'S1250200',
  'S1250300',
  'S1250400',
  'S1250500',
  'S1250600',
  'S1250700',
  'S1338900',
  'S1339000',
  'S1339200',
  'S1339300',
  'S1339400',
  'S1339500',
  'S1339600',
  'S1339700',
  'S1339800',
  'S1339900',
  'S1340000',
  'S1340100',
  'S1541200',
  'S1541400',
  'S1541700',
  'S1541900',
  'S1542400',
  'S1542500',
  'S1604500',
  'S1604600',
  'S1604700',
  'S1604800',
  'S1604900',
  'S1609200')

#Subsetting to just the variables we want
new_data <- new_data %>% 
  select(vars_R6) 

#Missing values
new_data[new_data == -1] = NA  # Refused
new_data[new_data == -2] = NA  # Dont know
new_data[new_data == -3] = NA  # Invalid missing
new_data[new_data == -4] = NA  # Valid missing
new_data[new_data == -5] = NA  # Non-interview 

#Factor variables  

#Sex
new_data$sex <- factor(new_data$R0536300,
    levels=c(0.0,1.0,2.0),
    labels=c("No Information",
      "Male",
      "Female")
  )

#Birthdate 
  #We don't have the date for their DOB, we will set to 1 for all participants.
new_data <- new_data %>%
  mutate(
    birthdate = make_date(
      year = R0536402,
      month = R0536401,
      day = 1
    )
  )  

unique(new_data$R0538600) 

#Ethnicity 
new_data$eth <- factor(new_data$R0538600,
    levels=c(0.0,1.0),
    labels=c("Non-Hispanic",
      "Hispanic")
  ) 

#Race 
new_data$race <- factor(new_data$R0538700,
    levels=c(0.0,1.0,2.0,3.0,4.0,5.0),
    labels=c("No information",
      "White",
      "Black or African American",
      "American Indian or Alaska Native",
      "Asian or Pacific Islander",
      "Other")
  ) 

#Race/ethnicity combined 
new_data$race_eth <- factor(new_data$R1482600,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Black",
      "Hispanic",
      "Mixed Race (Non-Hispanic)",
      "Non-Black / Non-Hispanic")
  ) 

#Mom parenting style 
new_data$mom_style <- factor(new_data$R1486500,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Uninvolved",
      "Permissive",
      "Authoritarian",
      "Authoritative")
  ) 

#Dad parenting style 
new_data$dad_style <- factor(new_data$R1486600,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Uninvolved",
      "Permissive",
      "Authoritarian",
      "Authoritative")
  )
 
#Parental Monitoring 
  #Note: It is cleaned in a way to make these variables categorical, but in the future we may need to have a numeric version so we could take an average over multiple years. We will therefore make two versions, one that is categorical and one that is numeric  

#Mom PMK   
new_data <- new_data %>%
  mutate(
    mom_pmk_97 = as.numeric(R1485700),
    mom_pmk_97_cat = case_when(
      between(mom_pmk_97, 0, 4) ~ "0 TO 4",
      between(mom_pmk_97, 5, 8) ~ "5 TO 8",
      between(mom_pmk_97, 9, 12) ~ "9 TO 12",
      between(mom_pmk_97, 13, 16) ~ "13 TO 16",
      TRUE ~ NA_character_
    ),
    mom_pmk_97_cat = factor(
      mom_pmk_97_cat,
      levels = c("0 TO 4", "5 TO 8", "9 TO 12", "13 TO 16")
    )
  )
  
#Dad PMK 
new_data <- new_data %>%
  mutate(
    dad_pmk_97 = as.numeric(R1485800),
    dad_pmk_97_cat = case_when(
      between(dad_pmk_97 , 0, 4) ~ "0 TO 4",
      between(dad_pmk_97 , 5, 8) ~ "5 TO 8",
      between(dad_pmk_97 , 9, 12) ~ "9 TO 12",
      between(dad_pmk_97 , 13, 16) ~ "13 TO 16",
      TRUE ~ NA_character_
    ),
    dad_pmk_97_cat = factor(
      dad_pmk_97_cat,
      levels = c("0 TO 4", "5 TO 8", "9 TO 12", "13 TO 16")
    )
  ) 

# Family/Home Risk Index 1997 
new_data <- new_data %>% 
  mutate(family_home_risk_cat = case_when(
          between(R1487000, 0, 399) ~ "0 TO 399", 
          between(R1487000, 400, 699) ~ "400 TO 699",
          between(R1487000, 700, 999) ~ "700 TO 999",
          between(R1487000, 1000, 1299) ~ "1000 TO 1299",
          between(R1487000, 1300, 1599) ~ "1300 TO 1599", 
          between(R1487000, 1600, 1899) ~ "1600 TO 1899", 
          between(R1487000, 1900, 2100) ~ "1900 TO 2100",
           TRUE ~ NA_character_
    ), 
      family_home_risk_num = as.numeric(R1487000)
         )

# Physical Environment Risk Index 1997 
new_data <- new_data %>% 
  mutate(physical_env_risk_cat = case_when(
          between(R1487100, 100, 299) ~ "100 TO 299", 
          between(R1487100, 300, 499) ~ "300 TO 499",
          between(R1487100, 500, 700) ~ "500 TO 700",
           TRUE ~ NA_character_
    ), 
      physical_env_risk_num = as.numeric(R1487100)
         )

# Substance Use Index 1997 
new_data$substance_use_index_cat <- factor(new_data$R1487800,
    levels=c(0.0,1.0,2.0,3.0),
    labels=c("0",
      "1",
      "2",
      "3")
  ) 

# Num Cigs Smoked/Day Last 30 Days 2002
new_data <- new_data %>% 
  rename(num_cigs_02 = S0921800)

#Age 1st Time Use other drugs 2002 
new_data <- new_data %>% 
  rename(age_first_drug_02 = S0923900) 

glimpse(new_data)

r6_2 <- new_data %>% 
  rename(id = R0000100) %>% 
  select(id, sex, birthdate, eth, race, race_eth,
         mom_pmk_97, mom_pmk_97_cat, dad_pmk_97, dad_pmk_97_cat, mom_style, dad_style, family_home_risk_cat, family_home_risk_num, physical_env_risk_cat, physical_env_risk_num, substance_use_index_cat, num_cigs_02, age_first_drug_02
         )

glimpse(r6_2) 

``` 


# Self Reported Drinking/Driving Data 

The self-reported drinking and driving data contains variables about 

