---
title: "01_Cleaning"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide  
---


```{r setup}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)
library(haven) 
library(labelled)


# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#importing functions
#source("functions.r")
``` 

# Introduction 

This script contains the code used to clean the raw datasets accessed from the NLSY97 contained within the `/RawData` directory. All datasets generated from this script will be saved in the `/CleanData` directory. 

A description of variables and project overview may be found in the project README. 
A data dictionary containing details about variables created may be accessed in the file `/CleanData/DataDictionary.xlsx`.

Functions used to clean the datasets may be accessed from the `/Scripts/functions.R` file.   

# Datasets 

## ALCUSE Data 

`"ALCUSE.dat"` contains descriptive variables about alcohol use. `R1235800` (Primary CV Sample Type), `S0922200` (Drank Since Last Interview 2002), `S0922300` (# Days drinking alcohol in last 30 days 2002), `S0922400` (# Drinks per day in last 30 days 2002), and `S0922600`(# Days drinking alcohol during school week 2002). None of these variables are intended to be in our models, but they may be useful for descriptive statistics.  

We will clean up these variables, applying formats and renaming them for ease of future use.  

```{r alcuse}
new_data <-  read.table('../RawData/ALCUSE.dat', sep=' ') 
names(new_data) <- c('R0000100', #Id
  'R1235800', #Cv samp
  'S0922200', #Drank since interview 02
  'S0922300', #Days drinking alc in last 30 
  'S0922400', #Num drinks per day
  'S0922600') #Num days drinking alc during school week

# Handle missing values

new_data[new_data == -1] = NA  # Refused
new_data[new_data == -2] = NA  # Dont know
new_data[new_data == -3] = NA  # Invalid missing
new_data[new_data == -4] = NA  # Valid missing
new_data[new_data == -5] = NA  # Non-interview

#Factor variables 

#CV Sample
new_data$R1235800 <- factor(new_data$R1235800,
    levels=c(0.0,1.0),
    labels=c("Oversample",
      "Cross-sectional")
  )

#Drank since last interview
new_data$S0922200 <- factor(new_data$S0922200,
    levels=c(0.0,1.0),
    labels=c("NO",
      "YES")
  )

#Num drinks per day in last 30 days  
range(new_data$S0922400, na.rm=TRUE) 
  #we have the option to change this into a factor variable, but this is probably better as a numeric descriptive stat.

```   

There are two variables that are factor variables according to the NLSY97 data dictionary and codes provided, but these variables are stored numerically, and there is not a whole lot of use in making them into categories. Below is the code to change them into factor variables, if we end up deciding to use them. 

```{r alcuse_factor_variables, eval = FALSE}  
#Factor option for Number of drinks per day
new_data$S0922400 <- factor(new_data$S0922400,
    levels=c(0.0,1.0,2.0,3.0,4.0,5.0,6.0,7.0,8.0,9.0,10.0,11.0,12.0,13.0,14.0,15.0),
    labels=c("0",
      "1",
      "2",
      "3",
      "4",
      "5",
      "6",
      "7",
      "8",
      "9",
      "10",
      "11",
      "12",
      "13",
      "14",
      "15+")
  ) 

#Factor option for number of days drinking alc during school week 
new_data <- new_data %>%
  mutate(
    S0922600 = case_when(
      between(S0922600, 1, 4)   ~ 1,
      between(S0922600, 5, 9)   ~ 5,
      between(S0922600, 10, 14) ~ 10,
      between(S0922600, 15, 19) ~ 15,
      between(S0922600, 20, 24) ~ 20,
      between(S0922600, 25, 29) ~ 25,
      TRUE ~ S0922600
    )
  )

  new_data$S0922600 <- factor(new_data$S0922600,
    levels=c(0.0,1.0,5.0,10.0,15.0,20.0,25.0,30.0),
    labels=c("0",
      "1 TO 4",
      "5 TO 9",
      "10 TO 14",
      "15 TO 19",
      "20 TO 24",
      "25 TO 29",
      "30")
  )

  #Factor option for number days drinking 
 new_data <- new_data %>%
  mutate(
    S0922300 = case_when(
      between(S0922300, 1, 4)   ~ 1,
      between(S0922300, 5, 9)   ~ 5,
      between(S0922300, 10, 14) ~ 10,
      between(S0922300, 15, 19) ~ 15,
      between(S0922300, 20, 24) ~ 20,
      between(S0922300, 25, 29) ~ 25,
      TRUE ~ S0922300
    )
  ) 
new_data$S0922300 <- factor(new_data$S0922300,
    levels=c(0.0,1.0,5.0,10.0,15.0,20.0,25.0,30.0),
    labels=c("0",
      "1 TO 4",
      "5 TO 9",
      "10 TO 14",
      "15 TO 19",
      "20 TO 24",
      "25 TO 29",
      "30")
  )

```
 
 
Lastly, we will rename our variable names with clearer naming conventions and save to a dataset called "alcuse" that we can then use when we merge our datasets. 

```{r renaming_alcuse_variables}
alcuse <- new_data
names(alcuse)<- c('id',
  'cv_samp',
  'drank_since_interview_02',
  'num_days_drink_02',
  'num_drinks_p_day_02',
  'num_days_drink_p_school_week') 
head(alcuse)
glimpse(alcuse)
```
 
## R6_2 Data 

This dataset contains a whole bunch of variables, many of which we do not need. We are only going to focus on retaining the variables pertaining to our study (there are some others included that I suspect may be useful descriptors or confounders).

```{r r6_2_dat} 
#variables we want 
vars_R6 <- c('R0000100', #id 
             "S1225800", #Rode with drinking driver
          'R0536300', #sex
          'R0536401', #bdate month
          'R0536402', #bdate year
          'R0538600', #ethnicity
          'R0538700', #race
          'R1204500', #annual income, 97
          'R1486500', #mom's parent style, 97
          'R1486600', #dad's parent style, 97
          'R1487000', #fam/home risk index 97
          'R1487100', #physical environment risk index 97
          'R1487800', #substance use index 1997
          'S0921800', # Num cigs smoked/day last 30 days
          'S0923900',#Age 1st time use oth drugs 2002
          'R1482600', #Race_ethnicity combined
          'S1542400') # Highest education level

new_data <- read.table('../RawData/R6_2.dat', sep=' ')
names(new_data) <- c('R0000100',
  'R0536300',
  'R0536401',
  'R0536402',
  'R0538600',
  'R0538700',
  'R1201300',
  'R1204500',
  'R1204700',
  'R1204900',
  'R1235800',
  'R1302400',
  'R1302500',
  'R1302600',
  'R1302700',
  'R1482600',
  'R1485700',
  'R1485800',
  'R1485900',
  'R1486000',
  'R1486100',
  'R1486200',
  'R1486300',
  'R1486400',
  'R1486500',
  'R1486600',
  'R1486700',
  'R1486800',
  'R1486900',
  'R1487000',
  'R1487100',
  'R1487200',
  'R1487300',
  'R1487400',
  'R1487500',
  'R1487600',
  'R1487700',
  'R1487800',
  'S0201500',
  'S0202000',
  'S0921600',
  'S0921700',
  'S0921800',
  'S0923700',
  'S0923900',
  'S0924000',
  'S0924100',
  'S0924200',
  'S1055500',
  'S1055600',
  'S1055800',
  'S1055900',
  'S1057000',
  'S1057100',
  'S1225600',
  'S1225700',
  'S1225800',
  'S1240700',
  'S1240800',
  'S1240801',
  'S1240802',
  'S1240803',
  'S1240804',
  'S1240805',
  'S1242800',
  'S1243100',
  'S1243200',
  'S1243201',
  'S1243202',
  'S1243203',
  'S1243204',
  'S1243205',
  'S1243206',
  'S1243207',
  'S1246500',
  'S1246600',
  'S1246601',
  'S1246602',
  'S1246603',
  'S1249300',
  'S1249400',
  'S1249401',
  'S1249402',
  'S1249600',
  'S1249900',
  'S1250100',
  'S1250200',
  'S1250300',
  'S1250400',
  'S1250500',
  'S1250600',
  'S1250700',
  'S1338900',
  'S1339000',
  'S1339200',
  'S1339300',
  'S1339400',
  'S1339500',
  'S1339600',
  'S1339700',
  'S1339800',
  'S1339900',
  'S1340000',
  'S1340100',
  'S1541200',
  'S1541400',
  'S1541700',
  'S1541900',
  'S1542400',
  'S1542500',
  'S1604500',
  'S1604600',
  'S1604700',
  'S1604800',
  'S1604900',
  'S1609200')

#Subsetting to just the variables we want
new_data <- new_data %>% 
  select(vars_R6) 

#Missing values
new_data[new_data == -1] = NA  # Refused
new_data[new_data == -2] = NA  # Dont know
new_data[new_data == -3] = NA  # Invalid missing
new_data[new_data == -4] = NA  # Valid missing
new_data[new_data == -5] = NA  # Non-interview 

#Factor variables  

#Sex
new_data$sex <- factor(new_data$R0536300,
    levels=c(0.0,1.0,2.0),
    labels=c("No Information",
      "Male",
      "Female")
  )

#Birthdate 
  #We don't have the date for their DOB, we will set to 1 for all participants.
new_data <- new_data %>%
  mutate(
    birthdate = make_date(
      year = R0536402,
      month = R0536401,
      day = 1
    )
  )  

unique(new_data$R0538600) 

#Ethnicity 
new_data$eth <- factor(new_data$R0538600,
    levels=c(0.0,1.0),
    labels=c("Non-Hispanic",
      "Hispanic")
  ) 

#Race 
new_data$race <- factor(new_data$R0538700,
    levels=c(0.0,1.0,2.0,3.0,4.0,5.0),
    labels=c("No information",
      "White",
      "Black or African American",
      "American Indian or Alaska Native",
      "Asian or Pacific Islander",
      "Other")
  ) 

#Race/ethnicity combined 
new_data$race_eth <- factor(new_data$R1482600,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Black",
      "Hispanic",
      "Mixed Race (Non-Hispanic)",
      "Non-Black / Non-Hispanic")
  ) 

#Mom parenting style 
new_data$mom_style <- factor(new_data$R1486500,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Uninvolved",
      "Permissive",
      "Authoritarian",
      "Authoritative")
  ) 

#Dad parenting style 
new_data$dad_style <- factor(new_data$R1486600,
    levels=c(1.0,2.0,3.0,4.0),
    labels=c("Uninvolved",
      "Permissive",
      "Authoritarian",
      "Authoritative")
  )
 

# Family/Home Risk Index 1997 
new_data <- new_data %>% 
  mutate(family_home_risk_cat = case_when(
          between(R1487000, 0, 399) ~ "0 TO 399", 
          between(R1487000, 400, 699) ~ "400 TO 699",
          between(R1487000, 700, 999) ~ "700 TO 999",
          between(R1487000, 1000, 1299) ~ "1000 TO 1299",
          between(R1487000, 1300, 1599) ~ "1300 TO 1599", 
          between(R1487000, 1600, 1899) ~ "1600 TO 1899", 
          between(R1487000, 1900, 2100) ~ "1900 TO 2100",
           TRUE ~ NA_character_
    ), 
      family_home_risk_num = as.numeric(R1487000)
         )

# Physical Environment Risk Index 1997 
new_data <- new_data %>% 
  mutate(physical_env_risk_cat = case_when(
          between(R1487100, 100, 299) ~ "100 TO 299", 
          between(R1487100, 300, 499) ~ "300 TO 499",
          between(R1487100, 500, 700) ~ "500 TO 700",
           TRUE ~ NA_character_
    ), 
      physical_env_risk_num = as.numeric(R1487100)
         )

# Substance Use Index 1997 
new_data$substance_use_index_cat <- factor(new_data$R1487800,
    levels=c(0.0,1.0,2.0,3.0),
    labels=c("0",
      "1",
      "2",
      "3")
  ) 

# Num Cigs Smoked/Day Last 30 Days 2002
new_data <- new_data %>% 
  rename(num_cigs_02 = S0921800)

#Age 1st Time Use other drugs 2002 
new_data <- new_data %>% 
  rename(age_first_drug_02 = S0923900)  
 
#Highest Education level 
new_data$education <- factor(new_data$S1542400,
    levels=c(0.0,1.0,2.0,3.0,4.0,5.0,6.0,7.0),
    labels=c("None",
      "GED",
      "High school diploma (Regular 12 year program)",
      "Associate/Junior college (AA)",
      "Bachelor's degree (BA, BS)",
      "Master's degree (MA, MS)",
      "PhD",
      "Professional degree (DDS, JD, MD)")
  )
   

#Rode with drinking driver 
unique(new_data$S1225800)  
new_data <- new_data %>% 
  mutate(
    ride_drink_2002 = factor(
      case_when(
        S1225800 == 1 ~ "No",
        S1225800 %in% 2:5 ~ "Yes",
        TRUE ~ NA_character_
      ),
      levels = c("No", "Yes")
    )
  )

glimpse(new_data)

r6_2 <- new_data %>% 
  rename(id = R0000100) %>% 
  select(id, sex, birthdate, eth, race, race_eth, mom_style, dad_style, family_home_risk_cat, family_home_risk_num, physical_env_risk_cat, physical_env_risk_num, substance_use_index_cat, num_cigs_02, age_first_drug_02, education, ride_drink_2002
         )

glimpse(r6_2) 

``` 


## Self Reported Drinking/Driving Data 

The self-reported drinking and driving data contains one variable of interest, being the number of times drivers reported driving when drinking in 2002. 

We are going to pull just the 02 year, since we want this year to maximize the individuals who are in both age groups (below and over 21 years old).   

## Inclusion Criteria 1

This is also going to involve our first inclusion criteria , where the indiviuals need to have reported driving the in the past 30 days and not have NA data. This is a primary variable of interest, so as we clean it, we will make note of how many individuals from the dataset are getting removed in this process. 

```{r drinking_driving_data_import, include = FALSE}
new_data <- read.table('../RawData/Self_Report_Drinking_Driving.dat', sep=' ')
names(new_data) <- c('R0000100',
'R0536300',
'R0536401',
'R0536402',
'R1235800',
'R1482600',
'S1225700',
'T1050200',
'T3145400',
'T4565700',
'T6209900',
'T7707300',
'U1100000',
'U2963200')


# Handle missing values

new_data[new_data == -1] = NA  # Refused
new_data[new_data == -2] = NA  # Dont know
new_data[new_data == -3] = NA  # Invalid missing
new_data[new_data == -4] = NA  # Valid missing
new_data[new_data == -5] = NA  # Non-interview

```
 
Let's see how many obs are in this df and only retain the variables we care about. 

According to the data cleaning code supplied by NLSY97, values of "6" in the data pertain to respondents who did not drive in the past 30 days.  

```{r drinking_driving_data_clean} 
glimpse(new_data) #8,984 obs 

new_data <- new_data %>% 
  rename(id = R0000100, 
         t_drive_drink_02 = S1225700) 

#how many NA Values for reported drinking/driving?? 
new_data %>% 
  summarize(n_na = sum(is.na(t_drive_drink_02)))
  #1098 

#how many respondents did not drive in the past 30 days? 
new_data %>% 
  filter(t_drive_drink_02== 6) %>% 
  summarize(n()) 
  #288

#Removing those respondents from the data 
new_data2 <- new_data %>% 
  filter(!is.na(t_drive_drink_02),
         t_drive_drink_02 != 6 )

nrow(new_data2) #7,598 rows, correct. 

``` 

Next we can create the driving after drinking variable we want to use for the study. "1" represents respondents who put "0" in as an answer, so they will be coded as 0 for our binary variable. All other respondents will be 1. 

```{r drinking_driving_data_clean_2} 
new_data3 <- new_data2 %>% 
  mutate(drive_after_drink = case_when(
    t_drive_drink_02 == 1 ~ 0, 
    t_drive_drink_02 %in% 2:5 ~1)
  ) %>% 
  select(drive_after_drink, id)
 
glimpse(new_data3) 

self_reported_drinking_driving <- new_data3
``` 

## Primary Data 
 
This one is a doozy. It has hundreds of variables. We are going to be very intentional here, only selecting the variables that are necessary to complete the analysis. 

If wanted, we can go back in and clean up additional variables, but note that the only variables included in the data dictionary document on this page will be the ones that are going to be in use. 

```{r primary_1, include = FALSE} 
data <- read.table('../RawData/Primary_Variables.dat', sep=' ') 
names(data) <- c('E0011406',
'E0011407',
'E0011408',
'E0011409',
'E0011410',
'E0011411',
'E0011412',
'E0011413',
'E0011414',
'E0011415',
'E0011416',
'E0011417',
'E0011418',
'E0011419',
'E0011420',
'E0011421',
'E0011422',
'E0011423',
'E0011424',
'E0011425',
'E0011426',
'E0011427',
'E0011428',
'E0011429',
'E0011430',
'E0011431',
'E0011432',
'E0011433',
'E0011434',
'E0011435',
'E0011436',
'E0011437',
'E0011438',
'E0011439',
'E0011440',
'E0011441',
'E0011442',
'E0011443',
'E0011444',
'E0011445',
'E0011446',
'E0011447',
'E0011448',
'E0011449',
'E0011450',
'E0011451',
'E0011452',
'E0011453',
'E0011501',
'E0011502',
'E0011503',
'E0011504',
'E0011505',
'E0011506',
'E0011507',
'E0011508',
'E0011509',
'E0011510',
'E0011511',
'E0011512',
'E0011513',
'E0011514',
'E0011515',
'E0011516',
'E0011517',
'E0011518',
'E0011519',
'E0011520',
'E0011521',
'E0011522',
'E0011523',
'E0011524',
'E0011525',
'E0011526',
'E0011527',
'E0011528',
'E0011529',
'E0011530',
'E0011531',
'E0011532',
'E0011533',
'E0011534',
'E0011535',
'E0011536',
'E0011537',
'E0011538',
'E0011539',
'E0011540',
'E0011541',
'E0011542',
'E0011543',
'E0011544',
'E0011545',
'E0011546',
'E0011547',
'E0011548',
'E0011549',
'E0011550',
'E0011551',
'E0011552',
'E0011601',
'E0011602',
'E0011603',
'E0011604',
'E0011605',
'E0011606',
'E0011607',
'E0011608',
'E0011609',
'E0011610',
'E0011611',
'E0011612',
'E0011613',
'E0011614',
'E0011615',
'E0011616',
'E0011617',
'E0011618',
'E0011619',
'E0011620',
'E0011621',
'E0011622',
'E0011623',
'E0011624',
'E0011625',
'E0011626',
'E0011627',
'E0011628',
'E0011629',
'E0011630',
'E0011631',
'E0011632',
'E0011633',
'E0011634',
'E0011635',
'E0011636',
'E0011637',
'E0011638',
'E0011639',
'E0011640',
'E0011641',
'E0011642',
'E0011643',
'E0011644',
'E0011645',
'E0011646',
'E0011647',
'E0011648',
'E0011649',
'E0011650',
'E0011651',
'E0011652',
'E0011701',
'E0011702',
'E0011703',
'E0011704',
'E0011705',
'E0011706',
'E0011707',
'E0011708',
'E0011709',
'E0011710',
'E0011711',
'E0011712',
'E0011713',
'E0011714',
'E0011715',
'E0011716',
'E0011717',
'E0011718',
'E0011719',
'E0011720',
'E0011721',
'E0011722',
'E0011723',
'E0011724',
'E0011725',
'E0011726',
'E0011727',
'E0011728',
'E0011729',
'E0011730',
'E0011731',
'E0011732',
'E0011733',
'E0011734',
'E0011735',
'E0011736',
'E0011737',
'E0011738',
'E0011739',
'E0011740',
'E0011741',
'E0011742',
'E0011743',
'E0011744',
'E0011745',
'E0011746',
'E0011747',
'E0011748',
'E0011749',
'E0011750',
'E0011751',
'E0011752',
'E0011801',
'E0011802',
'E0011803',
'E0011804',
'E0011805',
'E0011806',
'E0011807',
'E0011808',
'E0011809',
'E0011810',
'E0011811',
'E0011812',
'E0011813',
'E0011814',
'E0011815',
'E0011816',
'E0011817',
'E0011818',
'E0011819',
'E0011820',
'E0011821',
'E0011822',
'E0011823',
'E0011824',
'E0011825',
'E0011826',
'E0011827',
'E0011828',
'E0011829',
'E0011830',
'E0011831',
'E0011832',
'E0011833',
'E0011834',
'E0011835',
'E0011836',
'E0011837',
'E0011838',
'E0011839',
'E0011840',
'E0011841',
'E0011842',
'E0011843',
'E0011844',
'E0011845',
'E0011846',
'E0011847',
'E0011848',
'E0011849',
'E0011850',
'E0011851',
'E0011852',
'E0011901',
'E0011902',
'E0011903',
'E0011904',
'E0011905',
'E0011906',
'E0011907',
'E0011908',
'E0011909',
'E0011910',
'E0011911',
'E0011912',
'E0011913',
'E0011914',
'E0011915',
'E0011916',
'E0011917',
'E0011918',
'E0011919',
'E0011920',
'E0011921',
'E0011922',
'E0011923',
'E0011924',
'E0011925',
'E0011926',
'E0011927',
'E0011928',
'E0011929',
'E0011930',
'E0011931',
'E0011932',
'E0011933',
'E0011934',
'E0011935',
'E0011936',
'E0011937',
'E0011938',
'E0011939',
'E0011940',
'E0011941',
'E0011942',
'E0011943',
'E0011944',
'E0011945',
'E0011946',
'E0011947',
'E0011948',
'E0011949',
'E0011950',
'E0011951',
'E0011952',
'E0012001',
'E0012002',
'E0012003',
'E0012004',
'E0012005',
'E0012006',
'E0012007',
'E0012008',
'E0012009',
'E0012010',
'E0012011',
'E0012012',
'E0012013',
'E0012014',
'E0012015',
'E0012016',
'E0012017',
'E0012018',
'E0012019',
'E0012020',
'E0012021',
'E0012022',
'E0012023',
'E0012024',
'E0012025',
'E0012026',
'E0012027',
'E0012028',
'E0012029',
'E0012030',
'E0012031',
'E0012032',
'E0012033',
'E0012034',
'E0012035',
'E0012036',
'E0012037',
'E0012038',
'E0012039',
'E0012040',
'E0012041',
'E0012042',
'E0012043',
'E0012044',
'E0012045',
'E0012046',
'E0012047',
'E0012048',
'E0012049',
'E0012050',
'E0012051',
'E0012052',
'E0012053',
'E0012101',
'E0012102',
'E0012103',
'E0012104',
'E0012105',
'E0012106',
'E0012107',
'E0012108',
'E0012109',
'E0012110',
'E0012111',
'E0012112',
'E0012113',
'E0012114',
'E0012115',
'E0012116',
'E0012117',
'E0012118',
'E0012119',
'E0012120',
'E0012121',
'E0012122',
'E0012123',
'E0012124',
'E0012125',
'E0012126',
'E0012127',
'E0012128',
'E0012129',
'E0012130',
'E0012131',
'E0012132',
'E0012133',
'E0012134',
'E0012135',
'E0012136',
'E0012137',
'E0012138',
'E0012139',
'E0012140',
'E0012141',
'E0012142',
'E0012143',
'E0012144',
'E0012145',
'E0012146',
'E0012147',
'E0012148',
'E0012149',
'E0012150',
'E0012151',
'E0012152',
'E0012201',
'E0012202',
'E0012203',
'E0012204',
'E0012205',
'E0012206',
'E0012207',
'E0012208',
'E0012209',
'E0012210',
'E0012211',
'E0012212',
'E0012213',
'E0012214',
'E0012215',
'E0012216',
'E0012217',
'E0012218',
'E0012219',
'E0012220',
'E0012221',
'E0012222',
'E0012223',
'E0012224',
'E0012225',
'E0012226',
'E0012227',
'E0012228',
'E0012229',
'E0012230',
'E0012231',
'E0012232',
'E0012233',
'E0012234',
'E0012235',
'E0012236',
'E0012237',
'E0012238',
'E0012239',
'E0012240',
'E0012241',
'E0012242',
'E0012243',
'E0012244',
'E0012245',
'E0012246',
'E0012247',
'E0012248',
'E0012249',
'E0012250',
'E0012251',
'E0012252',
'E0012301',
'E0012302',
'E0012303',
'E0012304',
'E0012305',
'E0012306',
'E0012307',
'E0012308',
'E0012309',
'E0012310',
'E0012311',
'E0012312',
'E0012313',
'E0012314',
'E0012315',
'E0012316',
'E0012317',
'E0012318',
'E0012319',
'E0012320',
'E0012321',
'E0012322',
'E0012323',
'E0012324',
'E0012325',
'E0012326',
'E0012327',
'E0012328',
'E0012329',
'E0012330',
'E0012331',
'E0012332',
'E0012333',
'E0012334',
'E0012335',
'E0012336',
'E0012337',
'E0012338',
'E0012339',
'E0012340',
'E0012341',
'E0012342',
'E0012343',
'E0012344',
'E0012345',
'E0012346',
'E0012347',
'E0012348',
'E0012349',
'E0012350',
'E0012351',
'E0012352',
'E0012401',
'E0012402',
'E0012403',
'E0012404',
'E0012405',
'E0012406',
'E0012407',
'E0012408',
'E0012409',
'E0012410',
'E0012411',
'E0012412',
'E0012413',
'E0012414',
'E0012415',
'E0012416',
'E0012417',
'E0012418',
'E0012419',
'E0012420',
'E0012421',
'E0012422',
'E0012423',
'E0012424',
'E0012425',
'E0012426',
'E0012427',
'E0012428',
'E0012429',
'E0012430',
'E0012431',
'E0012432',
'E0012433',
'E0012434',
'E0012435',
'E0012436',
'E0012437',
'E0012438',
'E0012439',
'E0012440',
'E0012441',
'E0012442',
'E0012443',
'E0012444',
'E0012445',
'E0012446',
'E0012447',
'E0012448',
'E0012449',
'E0012450',
'E0012451',
'E0012452',
'E0012501',
'E0012502',
'E0012503',
'E0012504',
'E0012505',
'E0012506',
'E0012507',
'E0012508',
'E0012509',
'E0012510',
'E0012511',
'E0012512',
'E0012513',
'E0012514',
'E0012515',
'E0012516',
'E0012517',
'E0012518',
'E0012519',
'E0012520',
'E0012521',
'E0012522',
'E0012523',
'E0012524',
'E0012525',
'E0012526',
'E0012527',
'E0012528',
'E0012529',
'E0012530',
'E0012531',
'E0012532',
'E0012533',
'E0012534',
'E0012535',
'E0012536',
'E0012537',
'E0012538',
'E0012539',
'E0012540',
'E0012541',
'E0012542',
'E0012543',
'E0012544',
'E0012545',
'E0012546',
'E0012547',
'E0012548',
'E0012549',
'E0012550',
'E0012551',
'E0012552',
'E0012553',
'E0012601',
'E0012602',
'E0012603',
'E0012604',
'E0012605',
'E0012606',
'E0012607',
'E0012608',
'E0012609',
'E0012610',
'E0012611',
'E0012612',
'E0012613',
'E0012614',
'E0012615',
'E0012616',
'E0012617',
'E0012618',
'E0012619',
'E0012620',
'E0012621',
'E0012622',
'E0012623',
'E0012624',
'E0012625',
'E0012626',
'E0012627',
'E0012628',
'E0012629',
'E0012630',
'E0012631',
'E0012632',
'E0012633',
'E0012634',
'E0012635',
'E0012636',
'E0012637',
'E0012638',
'E0012639',
'E0012640',
'E0012641',
'E0012642',
'E0012643',
'E0012644',
'E0012645',
'E0012646',
'E0012647',
'E0012648',
'E0012649',
'E0012650',
'E0012651',
'E0012652',
'E0012701',
'E0012702',
'E0012703',
'E0012704',
'E0012705',
'E0012706',
'E0012707',
'E0012708',
'E0012709',
'E0012710',
'E0012711',
'E0012712',
'E0012713',
'E0012714',
'E0012715',
'E0012716',
'E0012717',
'E0012718',
'E0012719',
'E0012720',
'E0012721',
'E0012722',
'E0012723',
'E0012724',
'E0012725',
'E0012726',
'E0012727',
'E0012728',
'E0012729',
'E0012730',
'E0012731',
'E0012732',
'E0012733',
'E0012734',
'E0012735',
'E0012736',
'E0012737',
'E0012738',
'E0012739',
'E0012740',
'E0012741',
'E0012742',
'E0012743',
'E0012744',
'E0012745',
'E0012746',
'E0012747',
'E0012748',
'E0012749',
'E0012750',
'E0012751',
'E0012752',
'E0012801',
'E0012802',
'E0012803',
'E0012804',
'E0012805',
'E0012806',
'E0012807',
'E0012808',
'E0012809',
'E0012810',
'E0012811',
'E0012812',
'E0012813',
'E0012814',
'E0012815',
'E0012816',
'E0012817',
'E0012818',
'E0012819',
'E0012820',
'E0012821',
'E0012822',
'E0012823',
'E0012824',
'E0012825',
'E0012826',
'E0012827',
'E0012828',
'E0012829',
'E0012830',
'E0012831',
'E0012832',
'E0012833',
'E0012834',
'E0012835',
'E0012836',
'E0012837',
'E0012838',
'E0012839',
'E0012840',
'E0012841',
'E0012842',
'E0012843',
'E0012844',
'E0012845',
'E0012846',
'E0012847',
'E0012848',
'E0012849',
'E0012850',
'E0012851',
'E0012852',
'E0012901',
'E0012902',
'E0012903',
'E0012904',
'E0012905',
'E0012906',
'E0012907',
'E0012908',
'E0012909',
'E0012910',
'E0012911',
'E0012912',
'E0012913',
'E0012914',
'E0012915',
'E0012916',
'E0012917',
'E0012918',
'E0012919',
'E0012920',
'E0012921',
'E0012922',
'E0012923',
'E0012924',
'E0012925',
'E0012926',
'E0012927',
'E0012928',
'E0012929',
'E0012930',
'E0012931',
'E0012932',
'E0012933',
'E0012934',
'E0012935',
'E0012936',
'E0012937',
'E0012938',
'E0012939',
'E0012940',
'E0012941',
'E0012942',
'E0012943',
'E0012944',
'E0012945',
'E0012946',
'E0012947',
'E0012948',
'E0012949',
'E0012950',
'E0012951',
'E0012952',
'E0013001',
'E0013002',
'E0013003',
'E0013004',
'E0013005',
'E0013006',
'E0013007',
'E0013008',
'E0013009',
'E0013010',
'E0013011',
'E0013012',
'E0013013',
'E0013014',
'E0013015',
'E0013016',
'E0013017',
'E0013018',
'E0013019',
'E0013020',
'E0013021',
'E0013022',
'E0013023',
'E0013024',
'E0013025',
'E0013026',
'E0013027',
'E0013028',
'E0013029',
'E0013030',
'E0013031',
'E0013032',
'E0013033',
'E0013034',
'E0013035',
'E0013036',
'E0013037',
'E0013038',
'E0013039',
'E0013040',
'E0013041',
'E0013042',
'E0013043',
'E0013044',
'E0013045',
'E0013046',
'E0013047',
'E0013048',
'E0013049',
'E0013050',
'E0013051',
'E0013052',
'E0013101',
'E0013102',
'E0013103',
'E0013104',
'E0013105',
'E0013106',
'E0013107',
'E0013108',
'E0013109',
'E0013110',
'E0013111',
'E0013112',
'E0013113',
'E0013114',
'E0013115',
'E0013116',
'E0013117',
'E0013118',
'E0013119',
'E0013120',
'E0013121',
'E0013122',
'E0013123',
'E0013124',
'E0013125',
'E0013126',
'E0013127',
'E0013128',
'E0013129',
'E0013130',
'E0013131',
'E0013132',
'E0013133',
'E0013134',
'E0013135',
'E0013136',
'E0013137',
'E0013138',
'E0013139',
'E0013140',
'E0013141',
'E0013142',
'E0013143',
'E0013144',
'E0013145',
'E0013146',
'E0013147',
'E0013148',
'E0013149',
'E0013150',
'E0013151',
'E0013152',
'E0013153',
'E0013201',
'E0013202',
'E0013203',
'E0013204',
'E0013205',
'E0013206',
'E0013207',
'E0013208',
'E0013209',
'E0013210',
'E0013211',
'E0013212',
'E0013213',
'E0013214',
'E0013215',
'E0013216',
'E0013217',
'E0013218',
'E0013219',
'E0013220',
'E0013221',
'E0013222',
'E0013223',
'E0013224',
'E0013225',
'E0013226',
'E0013227',
'E0013228',
'E0013229',
'E0013230',
'E0013231',
'E0013232',
'E0013233',
'E0013234',
'E0013235',
'E0013236',
'E0013237',
'E0013238',
'E0013239',
'E0013240',
'E0013241',
'E0013242',
'E0013243',
'E0013244',
'E0013245',
'E0013246',
'E0013247',
'E0013248',
'E0013249',
'E0013250',
'E0013251',
'E0013252',
'E0013301',
'E0013302',
'E0013303',
'E0013304',
'E0013305',
'E0013306',
'E0013307',
'E0013308',
'E0013309',
'E0013310',
'E0013311',
'E0013312',
'E0013313',
'E0013314',
'E0013315',
'E0013316',
'E0013317',
'E0013318',
'E0013319',
'E0013320',
'E0013321',
'E0013322',
'E0013323',
'E0013324',
'E0013325',
'E0013326',
'E0013327',
'E0013328',
'E0013329',
'E0013330',
'E0013331',
'E0013332',
'E0013333',
'E0013334',
'E0013335',
'E0013336',
'E0013337',
'E0013338',
'E0013339',
'E0013340',
'E0013341',
'E0013342',
'E0013343',
'E0013344',
'E0013345',
'E0013346',
'E0013347',
'E0013348',
'E0013349',
'E0013350',
'E0013351',
'E0013352',
'E0013401',
'E0013402',
'E0013403',
'E0013404',
'E0013405',
'E0013406',
'E0013407',
'E0013408',
'E0013409',
'E0013410',
'E0013411',
'E0013412',
'E0013413',
'E0013414',
'E0013415',
'E0013416',
'E0013417',
'E0013418',
'E0013419',
'E0013420',
'E0013421',
'E0013422',
'E0013423',
'E0013424',
'E0013425',
'E0013426',
'E0013427',
'E0013428',
'E0013429',
'E0013430',
'E0013431',
'E0013432',
'E0013433',
'E0013434',
'E0013435',
'E0013436',
'E0013437',
'E0013438',
'E0013439',
'E0013440',
'E0013441',
'E0013442',
'E0013443',
'E0013444',
'E0013445',
'E0013446',
'E0013447',
'E0013448',
'E0013449',
'E0013450',
'E0013451',
'E0013452',
'E0013501',
'E0013502',
'E0013503',
'E0013504',
'E0013505',
'E0013506',
'E0013507',
'E0013508',
'E0013509',
'E0013510',
'E0013511',
'E0013512',
'E0013513',
'E0013514',
'E0013515',
'E0013516',
'E0013517',
'E0013518',
'E0013519',
'E0013520',
'E0013521',
'E0013522',
'E0013523',
'E0013524',
'E0013525',
'E0013526',
'E0013527',
'E0013528',
'E0013529',
'E0013530',
'E0013531',
'E0013532',
'E0013533',
'E0013534',
'E0013535',
'E0013536',
'E0013537',
'E0013538',
'E0013539',
'E0013540',
'E0013541',
'E0013542',
'E0013543',
'E0013544',
'E0013545',
'E0013546',
'E0013547',
'E0013548',
'E0013549',
'E0013550',
'E0013551',
'E0013552',
'E0013601',
'E0013602',
'E0013603',
'E0013604',
'E0013605',
'E0013606',
'E0013607',
'E0013608',
'E0013609',
'E0013610',
'E0013611',
'E0013612',
'E0013613',
'E0013614',
'E0013615',
'E0013616',
'E0013617',
'E0013618',
'E0013619',
'E0013620',
'E0013621',
'E0013622',
'E0013623',
'E0013624',
'E0013625',
'E0013626',
'E0013627',
'E0013628',
'E0013629',
'E0013630',
'E0013631',
'E0013632',
'E0013633',
'E0013634',
'E0013635',
'E0013636',
'E0013637',
'E0013638',
'E0013639',
'E0013640',
'E0013641',
'E0013642',
'E0013643',
'E0013644',
'E0013645',
'E0013646',
'E0013647',
'E0013648',
'E0013649',
'E0013650',
'E0013651',
'E0013652',
'E0013653',
'E0013701',
'E0013702',
'E0013703',
'E0013704',
'E0013705',
'E0013706',
'E0013707',
'E0013708',
'E0013709',
'E0013710',
'E0013711',
'E0013712',
'E0013713',
'E0013714',
'E0013715',
'E0013716',
'E0013717',
'E0013718',
'E0013719',
'E0013720',
'E0013721',
'E0013722',
'E0013723',
'E0013724',
'E0013725',
'E0013726',
'E0013727',
'E0013728',
'E0013729',
'E0013730',
'E0013731',
'E0013732',
'E0013733',
'E0013734',
'E0013735',
'E0013736',
'E0013737',
'E0013738',
'E0013739',
'E0013740',
'E0013741',
'E0013742',
'E0013743',
'E0013744',
'E0013745',
'E0013746',
'E0013747',
'E0013748',
'E0013749',
'E0013750',
'E0013751',
'E0013752',
'E0013801',
'E0013802',
'E0013803',
'E0013804',
'E0013805',
'E0013806',
'E0013807',
'E0013808',
'E0013809',
'E0013810',
'E0013811',
'E0013812',
'E0013813',
'E0013814',
'E0013815',
'E0013816',
'E0013817',
'E0013818',
'E0013819',
'E0013820',
'E0013821',
'E0013822',
'E0013823',
'E0013824',
'E0013825',
'E0013826',
'E0013827',
'E0013828',
'E0013829',
'E0013830',
'E0013831',
'E0013832',
'E0013833',
'E0013834',
'E0013835',
'E0013836',
'E0013837',
'E0013838',
'E0013839',
'E0013840',
'E0013841',
'E0013842',
'E0013843',
'E0013844',
'E0013845',
'E0013846',
'E0013847',
'E0013848',
'E0013849',
'E0013850',
'E0013851',
'E0013852',
'E0013901',
'E0013902',
'E0013903',
'E0013904',
'E0013905',
'E0013906',
'E0013907',
'E0013908',
'E0013909',
'E0013910',
'E0013911',
'E0013912',
'E0013913',
'E0013914',
'E0013915',
'E0013916',
'E0013917',
'E0013918',
'E0013919',
'E0013920',
'E0013921',
'E0013922',
'E0013923',
'E0013924',
'E0013925',
'E0013926',
'E0013927',
'E0013928',
'E0013929',
'E0013930',
'E0013931',
'E0013932',
'E0013933',
'E0013934',
'E0013935',
'E0013936',
'E0013937',
'E0013938',
'E0013939',
'E0013940',
'E0013941',
'E0013942',
'E0013943',
'E0013944',
'E0013945',
'E0013946',
'E0013947',
'E0013948',
'E0013949',
'E0013950',
'E0013951',
'E0013952',
'E0014001',
'E0014002',
'E0014003',
'E0014004',
'E0014005',
'E0014006',
'E0014007',
'E0014008',
'E0014009',
'E0014010',
'E0014011',
'E0014012',
'E0014013',
'E0014014',
'E0014015',
'E0014016',
'E0014017',
'E0014018',
'E0014019',
'E0014020',
'E0014021',
'E0014022',
'E0014023',
'E0014024',
'E0014025',
'E0014026',
'E0014027',
'E0014028',
'E0014029',
'E0014030',
'E0014031',
'E0014032',
'E0014033',
'E0014034',
'E0014035',
'E0014036',
'E0014037',
'E0014038',
'E0014039',
'E0014040',
'E0014041',
'E0014042',
'E0014043',
'E0014044',
'E0014045',
'E0014046',
'E0014047',
'E0014048',
'E0014049',
'E0014050',
'E0014051',
'E0014052',
'E0014101',
'E0014102',
'E0014103',
'E0014104',
'E0014105',
'E0014106',
'E0014107',
'E0014108',
'E0014109',
'E0014110',
'E0014111',
'E0014112',
'E0014113',
'E0014114',
'E0014115',
'E0014116',
'E0014117',
'E0014118',
'E0014119',
'E0014120',
'E0014121',
'E0014122',
'E0014123',
'E0014124',
'E0014125',
'E0014126',
'E0014127',
'E0014128',
'E0014129',
'E0014130',
'E0014131',
'E0014132',
'E0014133',
'E0014134',
'E0014135',
'E0014136',
'E0014137',
'E0014138',
'E0014139',
'E0014140',
'E0014141',
'E0014142',
'E0014143',
'E0014144',
'E0014145',
'E0014146',
'E0014147',
'E0014148',
'E0014149',
'E0014150',
'E0014151',
'E0014152',
'E0014201',
'E0014202',
'E0014203',
'E0014204',
'E0014205',
'E0014206',
'E0014207',
'E0014208',
'E0014209',
'E0014210',
'E0014211',
'E0014212',
'E0014213',
'E0014214',
'E0014215',
'E0014216',
'E0014217',
'E0014218',
'E0014219',
'E0014220',
'E0014221',
'E0014222',
'E0014223',
'E0014224',
'E0014225',
'E0014226',
'E0014227',
'E0014228',
'E0014229',
'E0014230',
'E0014231',
'E0014232',
'E0014233',
'E0014234',
'E0014235',
'E0014236',
'E0014237',
'E0014238',
'E0014239',
'E0014240',
'E0014241',
'E0014242',
'E0014243',
'E0014244',
'E0014245',
'E0014246',
'E0014247',
'E0014248',
'E0014249',
'E0014250',
'E0014251',
'E0014252',
'E0014253',
'E0014301',
'E0014302',
'E0014303',
'E0014304',
'E0014305',
'E0014306',
'E0014307',
'E0014308',
'E0014309',
'E0014310',
'E0014311',
'E0014312',
'E0014313',
'E0014314',
'E0014315',
'E0014316',
'E0014317',
'E0014318',
'E0014319',
'E0014320',
'E0014321',
'E0014322',
'E0014323',
'E0014324',
'E0014325',
'E0014326',
'E0014327',
'E0014328',
'E0014329',
'E0014330',
'E0014331',
'E0014332',
'E0014333',
'E0014334',
'E0014335',
'E0014336',
'E0014337',
'E0014338',
'E0014339',
'E0014340',
'E0014341',
'E0014342',
'E0014343',
'E0014344',
'E0014345',
'E0014346',
'E0014347',
'E0014348',
'E0014349',
'E0014350',
'E0014351',
'E0014352',
'E0014401',
'E0014402',
'E0014403',
'E0014404',
'E0014405',
'E0014406',
'E0014407',
'E0014408',
'E0014409',
'E0014410',
'E0014411',
'E0014412',
'E0014413',
'E0014414',
'E0014415',
'E0014416',
'E0014417',
'E0014418',
'E0014419',
'E0014420',
'E0014421',
'E0014422',
'E0014423',
'E0014424',
'E0014425',
'E0014426',
'E0014427',
'E0014428',
'E0014429',
'E0014430',
'E0014431',
'E0014432',
'E0014433',
'E0014434',
'E0014435',
'E0014436',
'E0014437',
'E0014438',
'R0000100',
'R0069100',
'R0322500',
'R0322700',
'R0358200',
'R0358700',
'R0359100',
'R0394300',
'R0394400',
'R0394500',
'R0394600',
'R0394700',
'R0394800',
'R0394900',
'R0395000',
'R0395100',
'R0395200',
'R0395300',
'R0395400',
'R0395500',
'R0395600',
'R0395700',
'R0395800',
'R0395900',
'R0536300',
'R0536401',
'R0536402',
'R1194100',
'R1204500',
'R1235800',
'R1482600',
'R1485700',
'R1485800',
'R1486100',
'R1486300',
'R1489700',
'R1489800',
'R2164100',
'R2164300',
'R2189600',
'R2190500',
'R2191300',
'R2211700',
'R2211800',
'R2211900',
'R2212000',
'R2212100',
'R2212200',
'R2212300',
'R2212400',
'R2212500',
'R2394600',
'R2553500',
'R2563201',
'R2563300',
'R2564101',
'R2601000',
'R2601100',
'R2601200',
'R2601300',
'R3482000',
'R3482200',
'R3508700',
'R3509600',
'R3510400',
'R3528800',
'R3528900',
'R3529000',
'R3529100',
'R3529200',
'R3529300',
'R3537600',
'R3537700',
'R3705100',
'R3876300',
'R3884801',
'R3884900',
'R3885701',
'R3924400',
'R3924500',
'R3924600',
'R3924700',
'R4880200',
'R4880400',
'R4906800',
'R4907700',
'R4908500',
'R4928900',
'R4929000',
'R4929100',
'R4929200',
'R4929300',
'R4929400',
'R4929500',
'R4929600',
'R4929700',
'R4946200',
'R4946300',
'R4946400',
'R4946500',
'R4946600',
'R4946700',
'R5160600',
'R5453700',
'R5464001',
'R5464100',
'R5464901',
'R5510900',
'R5511000',
'R5520100',
'R5520200',
'R5520300',
'R5520400',
'R5520500',
'R5520600',
'R5520700',
'R5520800',
'R5520900',
'R5521000',
'R5521100',
'R5521200',
'R6497600',
'R6497800',
'R6534300',
'R6535000',
'R6535700',
'R6557100',
'R6557200',
'R6557300',
'R6557400',
'R6557500',
'R6557600',
'R6557700',
'R6565200',
'R6565300',
'R6565400',
'R6565500',
'R6565600',
'R6578800',
'R6578900',
'R6579000',
'R6579100',
'R6579200',
'R6579300',
'R6888700',
'R7216000',
'R7227701',
'R7227800',
'R7228601',
'S0905500',
'S0905700',
'S0921800',
'S0922500',
'S0923300',
'S0945800',
'S0945900',
'S0946000',
'S0946100',
'S0946200',
'S0946300',
'S0946400',
'S0946500',
'S0953500',
'S0953600',
'S0953700',
'S0953800',
'S0965200',
'S0965300',
'S0965400',
'S0965500',
'S0965600',
'S1290100',
'S1531400',
'S1541601',
'S1541700',
'S1542501',
'S2001000',
'S2011401',
'S2011500',
'S2012301',
'S2978200',
'S2978400',
'S2988500',
'S2989200',
'S2989800',
'S2998700',
'S3005700',
'S3005800',
'S3005900',
'S3010900',
'S3011000',
'S3011100',
'S3011200',
'S3016100',
'S3016200',
'S3016300',
'S3016400',
'S3340800',
'S3801100',
'S3812301',
'S3812400',
'S3813801',
'S4677000',
'S4677200',
'S4683100',
'S4684000',
'S4684800',
'S4691608',
'S4692008',
'S4954500',
'S5401000',
'S5412700',
'S5412800',
'S5413400',
'S6309200',
'S6309400',
'S6318600',
'S6319600',
'S6320400',
'S6327408',
'S6327808',
'S6693600',
'S7501200',
'S7513600',
'S7513700',
'S7514300',
'S8330100',
'S8330300',
'S8333600',
'S8334100',
'S8334400',
'S8339708',
'S8340108',
'S8674800',
'T0008500',
'T0014000',
'T0014100',
'T0014700',
'T0737900',
'T0738100',
'T0740400',
'T0740900',
'T0741200',
'T0746508',
'T0746908',
'T1033600',
'T1094400',
'T2011100',
'T2016100',
'T2016200',
'T2016800',
'T2780200',
'T2780400',
'T2783900',
'T2784400',
'T2784700',
'T2790508',
'T2790908',
'T3144200',
'T3601500',
'T3606400',
'T3606500',
'T3607100',
'T4494600',
'T4494800',
'T4495600',
'T4496100',
'T4496400',
'T4502108',
'T4502508',
'T4561800',
'T5201400',
'T5206700',
'T5206800',
'T5206900',
'T5207400',
'T5207500',
'T6141700',
'T6141900',
'T6144500',
'T6145000',
'T6145300',
'T6151008',
'T6151408',
'T6206000',
'T6651300',
'T6656500',
'T6656600',
'T6656700',
'T6657200',
'T6657300',
'T7635600',
'T7635800',
'T7639000',
'T7639500',
'T7639800',
'T7645508',
'T7645908',
'T7703400',
'T8123600',
'T8128900',
'T8129000',
'T8129100',
'T8129600',
'T8129700',
'T9039300',
'T9045408',
'T9045808',
'T9092700',
'U0001800',
'U0008800',
'U0008900',
'U0009400',
'U1028700',
'U1032000',
'U1032300',
'U1036708',
'U1037108',
'U1096100',
'U1838500',
'U1845400',
'U1845500',
'U1846000',
'U2924108',
'U2924508',
'U2962700',
'U3437900',
'U3443900',
'U3444000',
'U3444500',
'U4329708',
'U4330008',
'U4368100',
'U4943000',
'U4949600',
'U4949700',
'U4950200',
'U4958700',
'U5825108',
'U5825408',
'U5833300',
'U5833301',
'U5833302',
'U5833303',
'U5833304',
'U5833305',
'U5833306',
'U5833307',
'U5833308',
'U5833309',
'U5833310',
'U5833311',
'U5833400',
'U5833401',
'U5833402',
'U5833403',
'U5833404',
'U5833405',
'U5833406',
'U5833407',
'U5833408',
'U5833409',
'U5833410',
'U5833411',
'U5833500',
'U5833501',
'U5833502',
'U5833503',
'U5833504',
'U5833505',
'U5833506',
'U5833507',
'U5833508',
'U5833509',
'U5833510',
'U5833511',
'U5833600',
'U5833601',
'U5833602',
'U5833603',
'U5833604',
'U5833605',
'U5833606',
'U5833607',
'U5833608',
'U5833609',
'U5833610',
'U5833611',
'U5860800',
'U6349900',
'U6356300',
'U6356400',
'U6356900',
'U7203908',
'U7204208',
'U7239400',
'U7239500',
'U7239900') 

# Handle missing values

data[data == -1] = NA  # Refused
data[data == -2] = NA  # Dont know
data[data == -3] = NA  # Invalid missing
data[data == -4] = NA  # Valid missing
data[data == -5] = NA  # Non-interview 

``` 

Now we are going to subset to only the variables we care about for this dataset. 

```{r primary_2}
primary_vars <- c("R0000100", #ID
                  "S0922500", #Binge Drinking
                  "S1531400", #Age at r6
                  "S0923300", #Marijuana use 
                  "S1541700", #Annual household income 2002 
                  "R1489700", #Stratum
                  "R1489800", #PSU
                  "R1485700", #mom pmk 97 
                  "R2601000", #mom pmk 98 
                  "R3924400", #mom pmk 99 
                  "R5510900", #mom pmk 00 
                  "R1485800", #dad pmk 97 
                  "R2601100", #dad pmk 98 
                  "R3924500", #dad pmk 99 
                  "R5511000"  #dad pmk 00
                  ) 

data2 <- data %>% 
  select(primary_vars) 
glimpse(data2) 

#Cleaning variables 

#Binge drinking 
data2 <- data2 %>% 
  mutate(binge = case_when(
    S0922500 == 0 ~ 0 ,
    S0922500 >= 1 ~ 1
  ))

# Age 
data2 <- data2 %>% 
  rename(age = S1531400) %>% 
  mutate(age_group = case_when(
    age < 21 ~ "Pre-21" ,
    age >= 21 ~ "21-24"
  )) 


#Marijuana Use  
data2 <- data2 %>% 
  mutate(marijuana = case_when(
    S0923300 == 0 ~ 0, 
    S0923300 >=1 ~ 1
  ))
  
 
#Annual Household income 2002 
data2 <- data2 %>% 
  mutate(
    income = case_when(
      is.na(S1541700) ~ NA_character_,
      S1541700 <= 10000 ~ "<=$10,000",
      S1541700 > 10000 & S1541700 <= 30000 ~ "$10,001 - $30,000",
      S1541700 > 30000 & S1541700 <= 50000 ~ "$30,001 - $50,000",
      S1541700 > 50000 & S1541700 <= 80000 ~ "$50,001 - $80,000",
      S1541700 > 80000 ~ ">$80,000"
    ),
    income = factor(
      income,
      levels = c(
        "<=$10,000",
        "$10,001 - $30,000",
        "$30,001 - $50,000",
        "$50,001 - $80,000",
        ">$80,000"
      )
    )
  )
 
#Parental Monitoring 

#We are going to retain 4 versions of pmk, which we will later decide what to do with. We will have our baseline pmk scores for mom and dad, and our average pmk scores. We will also further categorize these scores as categorical, to have that option. 


#Renaming Variables 
data2 <- data2 %>%
  rename(
mom_pmk_97	= R1485700,
mom_pmk_98 =	R2601000,
mom_pmk_99 =	R3924400,
mom_pmk_00 =	R5510900,
dad_pmk_97 =	R1485800, 
dad_pmk_98 =	R2601100,
dad_pmk_99 =	R3924500, 
dad_pmk_00 =	R5511000
)
 
#Making average pmk variables 
data2 <- data2 %>% 
  mutate(
    avg_mom_pmk = rowMeans(
      select(., mom_pmk_97, mom_pmk_98, mom_pmk_99, mom_pmk_00),
      na.rm = TRUE
    ),
    avg_dad_pmk = rowMeans(
      select(., dad_pmk_97, dad_pmk_98, dad_pmk_99, dad_pmk_00),
      na.rm = TRUE
    ),
    
    avg_mom_pmk = na_if(avg_mom_pmk, NaN),
    avg_dad_pmk = na_if(avg_dad_pmk, NaN)
  ) %>% 
  rename(
    baseline_mom_pmk = mom_pmk_97,
    baseline_dad_pmk = dad_pmk_97
  )



#Categorical variable function  
recat_pmk <- function(df, var, var_cat) {
  df %>%
    mutate(
      {{ var_cat }} := case_when(
        between({{ var }}, 0, 4) ~ "0 TO 4",
        between({{ var }}, 5, 8) ~ "5 TO 8",
        between({{ var }}, 9, 12) ~ "9 TO 12",
        between({{ var }}, 13, 16) ~ "13 TO 16",
        TRUE ~ NA_character_
      ),
      {{ var_cat }} := factor(
        {{ var_cat }},
        levels = c("0 TO 4", "5 TO 8", "9 TO 12", "13 TO 16")
      )
    )
}

data2 <- recat_pmk(data2,avg_mom_pmk, avg_mom_pmk_cat)
data2 <- recat_pmk(data2,avg_dad_pmk, avg_dad_pmk_cat)
data2 <- recat_pmk(data2,baseline_mom_pmk, baseline_mom_pmk_cat)
data2 <- recat_pmk(data2,baseline_dad_pmk, baseline_dad_pmk_cat)
  
data2 %>% 
  select(avg_mom_pmk, avg_mom_pmk_cat, baseline_mom_pmk,
         baseline_dad_pmk, baseline_mom_pmk_cat, baseline_dad_pmk_cat) %>% 
  slice(1:10)

#renaming variables and subsetting 

primary <- data2 %>% 
  rename(id = R0000100, 
         stratum = R1489700, 
         psu = R1489800) %>% 
  select(
  id, psu, stratum,
  age, age_group,
  binge, marijuana, income,

  avg_mom_pmk,
  avg_mom_pmk_cat,
  avg_dad_pmk,
  avg_dad_pmk_cat,

  baseline_mom_pmk,
  baseline_mom_pmk_cat,
  baseline_dad_pmk,
  baseline_dad_pmk_cat
)

```

Before we move on to the weighting variable, let's do a quick check to see how many observations we have for our baseline pmk vs. average, to see whether there is merit in keeping one or the other. 

```{r pmk_exploration}
data2 %>% 
  summarize(
    n_dad_b   = sum(is.na(baseline_dad_pmk)),
    n_mom_b   = sum(is.na(baseline_mom_pmk)),
    n_dad_avg = sum(is.na(avg_dad_pmk)),
    n_mom_avg = sum(is.na(avg_mom_pmk)), 
    
    both_missing_baseline = sum(
      is.na(baseline_mom_pmk) & is.na(baseline_dad_pmk)
    ),
    
    both_missing_avg = sum(
      is.na(avg_mom_pmk) & is.na(avg_dad_pmk)
    )
  )

```
It looks like for our baseline participants, 5,025 are missing dad, 3,769 are missing mom, and 3,622 are missing both. 

When we take the average, 4,665 are missing dad, 3,642 are missing mom, and 3,572 are missing both.  

That means that for the *baseline* pmk data, we are missing **~40-55%** of data, whereas for the *average* pmk data, we are missing **39-52%** of data.

## Weighting variable 

This data seems relatively simple, just the two columns, one for ID and one for the weight. 

```{r weighting_data}
weight_data <- read_table('../RawData/Round6Weight.dat', col_names = FALSE )
names(weight_data) <- c("id", "weight") 
weight_data %>% 
  slice(1:10)
```  
There are only 7896 observations though??? Interestingly enough it goes until participant id 9022. Can we assume that the missing weights are due to them being appropriately sampled??? 


# Merging datasets 

Now we can merge all of our datasets with the variables. We need to make sure we join into the dataset with reported drinking and driving, since we have already applied inclusion criteria to that group. We will continue with further inclusion criteria later on. 

We will start by checking out how many columns and rows are in each df so we can be sure the merge is successful. 

```{r merge}
dim(self_reported_drinking_driving)  
  #2 cols, 7,598 rows
dim(alcuse) 
  #6 cols, 8,984 rows
dim(r6_2) 
  #21 cols, 8,984 rows
dim(primary) 
  #8 cols, 8,984 rows

merged <- left_join(self_reported_drinking_driving, alcuse, by = "id")  
dim(merged)

merged2 <- left_join(merged, r6_2, by = "id")
dim(merged2) 

merged3 <- left_join(merged2, primary, by = "id")
dim(merged3) 

glimpse(merged3)  

merged4 <- left_join(merged3, weight_data, by = "id") 
merged4 %>% 
  filter(is.na(weight)) %>% 
  nrow()  #there appears to be no missing weight data, interesting...

merged4 %>% 
  select(id, weight) %>% 
  tail()
```  

# Inclusion/Exclusion 

We previously applied exclusion criteria pertaining to our outcome variable of interest, drive_after_drink. 

We started with 8,984 observations. 
  We removed **1098** NA values for driving after drinking, and **288** individuals who did not report driving in the past 30 days. 

Additional inclusion criteria: 

- Had the survey design variables 

- Had the Round 6 weight  

```{r inclusion}
#how many have survey design var 
merged4 %>% 
  filter(is.na(cv_samp)) %>% 
  nrow()

#how many have round 6 weight
merged4 %>% 
  filter(is.na(weight)) %>% 
  nrow()
```

There are no missing values for these criteria, so we don't need to exclude any observations here.  

# Variable Labeling/Informats  

Before moving on to saving our dataset, we will apply some labeling and informats to them. 

```{r var_labels}
var_label(merged4$id) <- "Respondent ID"
var_label(merged4$drive_after_drink) <- "Drove after drinking alcohol in past 30 days (2002)"
var_label(merged4$age) <- "Age at Round 6 (2002)"
var_label(merged4$binge) <- "Binge Drinking - Consumed 5+ drinks on one occasion in past 30 days"
var_label(merged4$marijuana) <- "Used marijuana in past 30 days"
var_label(merged4$weight) <- "Round 6 survey weight"
var_label(merged4$stratum) <- "Sampling stratum"
var_label(merged4$psu) <- "Primary sampling unit" 

# PMK Variables  
var_label(merged4$baseline_dad_pmk) <- "Baseline (1997) Parental Monitoring Knowledge -- Residential Fathers"
var_label(merged4$baseline_mom_pmk) <- "Baseline (1997) Parental Monitoring Knowledge -- Residential Mothers" 
var_label(merged4$avg_dad_pmk) <- "Average Parental Monitoring Knowledge (1997-2000) -- Residential Fathers" 
var_label(merged4$avg_mom_pmk) <- "Average Parental Monitoring Knowledge (1997-2000) -- Residential Mothers"  



 
#Recategorizing Age Group for SAS 
merged4 <- merged4 %>%
  mutate(
    age_group = labelled(
      ifelse(age < 21, 1, 2),
      labels = c(
        "Pre-21" = 1,
        "21-24" = 2
      )
    )
  )

#Labelling binary vars
merged4$drive_after_drink <- labelled(
  merged4$drive_after_drink,
  labels = c(
    "No" = 0,
    "Yes" = 1
  )
) 

merged4$binge <- labelled(
  merged4$binge,
  labels = c(
    "No times" = 0,
    "≥ 1 time" = 1
  )
) 

merged4$marijuana <- labelled(
  merged4$marijuana,
  labels = c(
    "No times" = 0,
    "≥ 1 time" = 1
  )
)

```

# Saving final dataset  

We will save two versions, one as a .csv and one as a sas file. 

```{r save} 
write_csv(merged4, "../CleanData/study_dat.csv")

write_sas(
  merged4,
  "../CleanData/study_dat.sas7bdat"
)

write_xpt(
  merged4,
  "../CleanData/study_dat.xpt"
)
```
