---
title: "02_Exploration"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide  
---

```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)
library(haven) 
library(labelled) 
library(finalfit) 
library(naniar) 
library(purrr)
library(janitor)
library(skimr) 
library(survey)


# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load data 
study_dat <- read.csv("../CleanData/study_dat.csv") 

# Variable Labels  

var_label(study_dat$id) <- "Respondent ID"

var_label(study_dat$stratum) <- "Sampling stratum"
var_label(study_dat$psu) <- "Primary sampling unit"
var_label(study_dat$weight) <- "Round 6 survey weight"

var_label(study_dat$age) <- "Age at Round 6 (2002)"
var_label(study_dat$age_group) <- "Age group"

var_label(study_dat$drive_after_drink) <- 
  "Drove after drinking alcohol in past 30 days"

var_label(study_dat$binge) <- 
  "Consumed 5+ drinks on one occasion in past 30 days"

var_label(study_dat$marijuana) <- 
  "Used marijuana in past 30 days"

var_label(study_dat$sex) <- "Biological sex"
var_label(study_dat$eth) <- "Ethnicity"
var_label(study_dat$race) <- "Race"
var_label(study_dat$race_eth) <- "Combined race/ethnicity"

var_label(study_dat$income) <- 
  "Annual household income (previous year)"

var_label(study_dat$education) <- 
  "Highest educational attainment"

var_label(study_dat$ride_drink_2002) <- 
  "Rode with drinking driver in 2002"

var_label(study_dat$family_home_risk_num) <- 
  "Family/home risk index (numeric)"

var_label(study_dat$family_home_risk_cat) <- 
  "Family/home risk index category"

var_label(study_dat$physical_env_risk_num) <- 
  "Physical environment risk index (numeric)"

var_label(study_dat$physical_env_risk_cat) <- 
  "Physical environment risk index category"

var_label(study_dat$substance_use_index_cat) <- 
  "Substance use index"

var_label(study_dat$num_cigs_02) <- 
  "Number of cigarettes smoked in past 30 days (2002)"

var_label(study_dat$age_first_drug_02) <- 
  "Age first used other drugs"

var_label(study_dat$baseline_mom_pmk) <- 
  "Baseline maternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_dad_pmk) <- 
  "Baseline paternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_mom_pmk_cat) <- 
  "Baseline maternal PMK category"

var_label(study_dat$baseline_dad_pmk_cat) <- 
  "Baseline paternal PMK category"

var_label(study_dat$avg_mom_pmk) <- 
  "Average maternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_dad_pmk) <- 
  "Average paternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_mom_pmk_cat) <- 
  "Average maternal PMK category"

var_label(study_dat$avg_dad_pmk_cat) <- 
  "Average paternal PMK category"

var_label(study_dat$license) <- 
  "Driver's License Status"  

var_label(study_dat$avg_pmk) <- 
  "Average PMK both Parents 1999-2000"

# Binary Variable Labels 

study_dat <- study_dat %>%
  mutate(

    drive_after_drink = factor(
      drive_after_drink,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    binge = labelled(
      binge,
      labels = c(
        "No" = 0,
        "Yes" = 1
      )
    ),

    marijuana = labelled(
      marijuana,
      labels = c(
        "No" = 0,
        "Yes" = 1
      )
    )

  )

# Ordered Factors 
study_dat <- study_dat %>%
  mutate(

    age_group = factor(
      age_group,
      levels = c("Pre-21", "21-24")
    ),

    income = factor(
      income,
      levels = c(
        "<=$10,000",
        "$10,001 - $30,000",
        "$30,001 - $50,000",
        "$50,001 - $80,000",
        ">$80,000"
      ),
      ordered = TRUE
    ),

    baseline_mom_pmk_cat = factor(
      baseline_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    baseline_dad_pmk_cat = factor(
      baseline_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    avg_mom_pmk_cat = factor(
      avg_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    avg_dad_pmk_cat = factor(
      avg_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    )

  )

``` 


# Introduction 

This script contains the code used to explore the NLSY97 data that was previously cleaned in the `"01_Cleaning.rmd"` file. The primary goals of this script are to: 

1. Explore patterns of **missingness**, using cluster analysis and logistic regression to identify variables (including outcome) associated with the likelihood of missingness. 

2. Examine **variable distribution**, paying attention to possible outliers or colinear patterns.  This will help us decide which variables to include in our Table 1. It will also help us understand whether our variables meet the assumptions of the logistic regression models we plan to use later on. 

3. **Descriptive statistics** of population. We will retain some of these same descriptive statistics later on in our formal Analysis, but we will start by being more thorough in this document.  

# 1. Missingness   

To start, we are going to explore whether we have any missing data that depends on our outcome of interest (driving after drinking). We are going to have two explanatory vectors, the first containing our primary explanatory variable of interest and participant demographics, the second containing virtually all variables.

```{r missing_1}
# Examine with ff_glimpse
explanatory1 = c("age_group", "sex", 
  "race_eth", "education",  
  "binge", "marijuana", "income", "avg_mom_pmk", 
  "avg_dad_pmk", "avg_pmk")
dependent = "drive_after_drink" 

#other descriptive variables
explanatory2 = c("drank_since_interview_02", "num_days_drink_02", 
  "num_drinks_p_day_02", "num_days_drink_p_school_week",  
  "eth", "race", "mom_style", "dad_style", 
  "family_home_risk_num", "physical_env_risk_num",
  "substance_use_index_cat", "num_cigs_02", "age_first_drug_02", "ride_drink_2002")


#primary variables
study_dat %>% 
  ff_glimpse(dependent, explanatory1)  

#secondary variables 
study_dat %>% 
  ff_glimpse(dependent, explanatory2)   

#Missing data information 
miss_var_summary(study_dat) 

#Mcar test  
mcar_vars <- study_dat %>% 
  select(age_group, sex, race_eth, education, binge, income, marijuana, avg_mom_pmk, avg_dad_pmk, drive_after_drink)
mcar_test(mcar_vars)  

``` 


We got a significant MCAR test among our **primary variables** (x^2 = 9,055.96, p~0, missing patterns = 32). This indicates that we might be better off using multiple imputation, which was also mentioned as a method in the study protocol.   

## 1.1 Cluster Analysis  

We are going to use the naniar's package to make some data visualizations to help understand the patterns of missingness. 

```{r missing_2} 
#Headmap of dataset 
vis_miss(study_dat) 

# Sorting columns by missingness and cluster rows 
#Headmap of dataset 
vis_miss(study_dat, sort_miss = TRUE, cluster = TRUE)  

#Which variables have the most missing values? 
gg_miss_var(study_dat, show_pct = TRUE) 

#What about in terms of driving and drinking?
gg_miss_var(study_dat, facet = drive_after_drink, show_pct = TRUE) 

#Missing data visualization  
gg_miss_fct(study_dat, drive_after_drink)

```

When we look at the missing data by our outcome, driving after drinking, we see that there are some differences in missingness by **parental monitoring, binge drinking, family home risk, marijuana use, number of cigs in 02, number days drinking in 02, and phys environment risk.** 


## 1.2 Logistic regression  

Next, we want to fit logistic regression models that identify variables (including our outcome) that are associated with the likelihood of missingness.  

There are no missing data for our outcome variable, so we fortunately do not need to worry about that. However, we do want to check on whether the levels of drive after drink is associated with our other predictors. If our demographic/substance variables predict missingness, then missingness will be related to the observed data (consistent with MAR). If drive after drink predicts missingness, then it will depend on the outcome, and we will need to handle our values with multiple imputation or possibly deletion. 

```{r missing_logistic}
# Missingness indicator for outcome
vars_to_check <- c(
  "age_group", "sex", "race_eth", "education",
  "binge", "marijuana", "income",
  "avg_mom_pmk", "avg_dad_pmk", "avg_pmk",
  "drank_since_interview_02",
  "num_days_drink_02",
  "num_drinks_p_day_02",
  "num_days_drink_p_school_week",
  "eth", "race", "mom_style", "dad_style",
  "family_home_risk_num",
  "physical_env_risk_num",
  "substance_use_index_cat",
  "num_cigs_02",
  "age_first_drug_02",
  "ride_drink_2002"
) 

results <- list()

for(v in vars_to_check){

  # Skip variables with no missingness
  if(sum(is.na(study_dat[[v]])) == 0) next

  miss_var <- paste0("miss_", v)

  study_dat[[miss_var]] <- ifelse(
    is.na(study_dat[[v]]),
    1, 0
  )

  form <- as.formula(
    paste(
      miss_var,
      "~ drive_after_drink + age_group + sex + race_eth"
    )
  )

  model <- glm(
    form,
    data = study_dat,
    family = binomial
  )

  results[[v]] <- summary(model)

  cat("\n========================\n")
  cat("Missingness model for:", v, "\n")
  print(summary(model))
}


``` 

When we look at the results, we have some evidence to suggest that our data are not MCAR, because the missingness is associated with participant characteristics or the outcome. This is supported by our visual inspections earlier. 

Our missingness is likely MAR, supporting the use of multiple imputation.   

**Exposure-related missingness**

We saw consistent significance for age groups, for instance. Participants aged 21-24 had different probabilities of missingness than younger participants. Older participants may have been less likely to complete certain measures (for example, the parent/family measures of PMK).  

**Outcome-related missingness**  
Binge, marijuana, number days drinking, number cigs, and dad style are variables that had missingness associated with drive after drink. 

For instance, with binge drinking, participants who drove after drinking were less likely to have missing binge data. Perhaps participants were more forthcoming about their substance use than others, leading to this pattern. 

**Race/Ethnicity Patterns** 

Race/ethnicity predicted missingness for binge variables, dad pmk and parenting style, and alcohol use variables. 


**Summary** 

Missingness for several explanatory variables was associated with demographic characteristics and for some variables, our outcome. Data were unlikely to be missing at random (MCAR), and are more consistent with missing at random (MAR) mechanism. 

# 2. Variable Exploration 

## 2.1 Variable Distributions 

Next we are going to take a glimpse at our variable distributions. 

```{r var_skim} 
skim(study_dat) 
``` 

Let's take a closer look at some of our key variables.  

### Driving after Drinking (Outcome)

```{r}
ggplot(study_dat, aes(x = drive_after_drink)) +
  geom_bar() +
  labs(
    title = "Driving After Drinking",
    x = "Response",
    y = "Count"
  ) +
  theme_minimal() 

study_dat %>% 
  group_by(drive_after_drink) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)

```

### Age Group (Exposure)

```{r}
ggplot(study_dat, aes(x = age_group)) +
  geom_bar() +
  labs(
    title = "Age Group",
    x = "Age",
    y = "Count"
  ) +
  theme_minimal() 

study_dat %>% 
  group_by(age_group) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)

```

### Demographic Factors

```{r}
study_dat %>% 
  group_by(race_eth) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(sex) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(education) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)

study_dat %>% 
  group_by(income) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)

```

**Summary** 

- Majority Non-Black/Non-Hispanic (52%), followed by Black (25%). Will be accounted for with weighting. 
- Almost even sex split 
- Majority high school diplomat (69%), followed by None, which would likely account for those still in high school? Need to double check. 
- Income Majority NA, which would make sense for younger respondents not knowing the answer. After that, relatively even split betwen 10k-30k and >80k.

### Substance Use Factors

```{r}
study_dat %>% 
  group_by(ride_drink_2002) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(age_first_drug_02) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(num_cigs_02) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(substance_use_index_cat) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(num_days_drink_02) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(marijuana) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(binge) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)

```
**Summary** 

- Majority didn't report RWI 
- Missing basically all data (99.9%) of age of first drug use (reported in 2002). Going to exclude this variable from analysis due to that. 
- Num of cigs most frequent is NA (rather than 0, people most likely are skipping this question in this instance). We are missing data on 62% of respondents because of this. It may be more useful to categorize this information as smoker vs. non-smoker, as the exact number is likely due to all sorts of recall and social desirability biases.  
- Most are in the substance use index category of 0 (46%), and we are actually not missing much data (0.22%). This index is unfortunately only useful inasmuch as people also reported using marijuana, as this question more broadly pertains to whether respondents have increased using substances since the last round. 
- Num days drinking is majority missing (31%). 
- Missing a lott of data for marijuana (75%), which is unfortunate because we wanted to use it as an explanatory variable.
- Binge drinking also has a lot of missing data (42%), but there are more resondents who reported binge drinking than not binge drinking in the last 30 days. 


### Familial/Environmental Factors 


```{r}
study_dat %>% 
  group_by(avg_pmk_cat) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total= sum(n), 
         percent = (n/total)*100)

study_dat %>% 
  group_by(mom_style) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(dad_style) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(family_home_risk_cat) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100) 

study_dat %>% 
  group_by(physical_env_risk_cat) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(total = sum(n), 
         percent = (n/total)*100)
```
**Summary** 

- 50% Missing PMK information. Of that available, 23% is 9-12 (second highest monitoring), followed by 5 to 8 (second lowest monitoring). So right in the middle. 
- Majority authoritative mom parenting style, which is nice. Second highest is permissive, though, which is interesting for this sample in terms of if that differed for driving and drinking outcomes. 
- Dad style follows same trends as maternal, however we have a lot more NAs for this. 
- Lots of missing data for family home risk category, however highest cateogry is the lowest risk. 
- Physical risk environment also lots of missing data, but highest proportion is the lowest risk range. 

## 2.2 Logistic regression assumptions 

To run our logistic regression models, we need to meet the following assumptions: 

**1. Binary outcome** -- our outcome of driving after drinking meets this assumption

**2. Independence of observations** -- this is not a repeated measures model, each observation corresponds to one resondent and their answers during round 6 of the interview (unless looking at items collected historically/at baseline like race/ethnicity)

**3. No perfect multicollinearity** -- no variables can be perfectly colinear. We will check for colinearity of predictors that are naturally occurring, and we will keep in mind that many of our variables that we created by hand need to only include one version (ex, not including both baseline and avg PMK). 

We cann test this assumption by obtaining a VIF number from our model object after we have fit it (VIF > 5-10 indicates problematic multicollinearity). To do this, we will need to use the package `car`. 

**4. Linearity of the logit** -- the relationship between continuous predictors and the log-odds must be linear  

We can test this assumption after fitting the model with the Box-Tidwell test, where a p-value < 0.05 indicates a violation of the linearity assumption. 
To do this, we will need to use the package `ResourceSelection`. 

# 3. Descriptive Statistics  

We are going to compare our sample statistics before and after applying weighting variables for our variables of interest. 

## 3.1 Entire Sample  

### Unweighted 

### Weighted

## 3.2 Age-Group Specific 

## 3.3 Drinking while driving specific


