---
title: "03_Analysis"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide
---


```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)
library(haven) 
library(labelled) 
library(finalfit) 
library(naniar) 
library(purrr)
library(janitor)
library(skimr) 
library(survey) 
library(table1) 
library(tableone)
library(gtsummary)


# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load data 
study_dat <- read.csv("../CleanData/study_dat.csv") 

# Variable Labels  

var_label(study_dat$id) <- "Respondent ID"

var_label(study_dat$stratum) <- "Sampling stratum"
var_label(study_dat$psu) <- "Primary sampling unit"
var_label(study_dat$weight) <- "Round 6 survey weight"

var_label(study_dat$age) <- "Age at Round 6 (2002)"
var_label(study_dat$age_group) <- "Age group"

var_label(study_dat$drive_after_drink) <- 
  "Drove after drinking alcohol in past 30 days"

var_label(study_dat$binge) <- 
  "Consumed 5+ drinks on one occasion in past 30 days"

var_label(study_dat$marijuana) <- 
  "Used marijuana in past 30 days"

var_label(study_dat$sex) <- "Biological sex"
var_label(study_dat$eth) <- "Ethnicity"
var_label(study_dat$race) <- "Race"
var_label(study_dat$race_eth) <- "Combined race/ethnicity"

var_label(study_dat$income) <- 
  "Annual household income (previous year)"

var_label(study_dat$education) <- 
  "Highest educational attainment"

var_label(study_dat$ride_drink_2002) <- 
  "Rode with drinking driver in 2002"

var_label(study_dat$family_home_risk_num) <- 
  "Family/home risk index (numeric)"

var_label(study_dat$family_home_risk_cat) <- 
  "Family/home risk index category"

var_label(study_dat$physical_env_risk_num) <- 
  "Physical environment risk index (numeric)"

var_label(study_dat$physical_env_risk_cat) <- 
  "Physical environment risk index category"

var_label(study_dat$substance_use_index_cat) <- 
  "Substance use index"

var_label(study_dat$num_cigs_02) <- 
  "Number of cigarettes smoked in past 30 days (2002)"

var_label(study_dat$age_first_drug_02) <- 
  "Age first used other drugs"

var_label(study_dat$baseline_mom_pmk) <- 
  "Baseline maternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_dad_pmk) <- 
  "Baseline paternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_mom_pmk_cat) <- 
  "Baseline maternal PMK category"

var_label(study_dat$baseline_dad_pmk_cat) <- 
  "Baseline paternal PMK category"

var_label(study_dat$avg_mom_pmk) <- 
  "Average maternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_dad_pmk) <- 
  "Average paternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_mom_pmk_cat) <- 
  "Average maternal PMK category"

var_label(study_dat$avg_dad_pmk_cat) <- 
  "Average paternal PMK category"

var_label(study_dat$license) <- 
  "Driver's License Status"  

var_label(study_dat$avg_pmk) <- 
  "Average PMK both Parents 1999-2000"

# Binary Variable Labels 

study_dat <- study_dat %>%
  mutate(

    drive_after_drink = factor(
      drive_after_drink,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    binge = factor(
      binge,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    marijuana = factor(
      marijuana,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ) , 
    
    sex = factor(
      sex, 
      levels = c(1,0), 
      labels = c("Male", "Female")
    ), 
    
    smoker = factor(
      smoker, 
      levels = c(0,1), 
      labels = c("No", "≥ 1 Cig in Last 30 Days")
    ), 

    license = factor(
      license, 
      levels = c(0,1), 
      labels = c("Unlicensed", "Licensed")
    ), 
    
   ride_drink_2002 =factor(
      ride_drink_2002, 
      levels = c(0,1), 
      labels = c("No", "Yes")
    )
    
  )

# Ordered Factors 
study_dat <- study_dat %>%
  mutate(

    age_group = factor(
      age_group,
      levels = c("Pre-21", "21-24")
    ),

    income = factor(
      income,
      levels = c(
        "<=$10,000",
        "$10,001 - $30,000",
        "$30,001 - $50,000",
        "$50,001 - $80,000",
        ">$80,000"
      ),
      ordered = TRUE
    ),

    baseline_mom_pmk_cat = factor(
      baseline_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    baseline_dad_pmk_cat = factor(
      baseline_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    avg_mom_pmk_cat = factor(
      avg_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    ),

    avg_dad_pmk_cat = factor(
      avg_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = TRUE
    )
    
  )


design <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
) 
``` 

# Introduction 
 
 This script contains the code used to explore the NLSY97 data that was previously cleaned in the `"01_Cleaning.rmd"` file. The primary goals of this script are to: 

1. Generate **descriptive statistics** of the sample stratified by the exposure (age group), producing a table 1 with weighted (nationally representative) values

2. **Sequential logistic models** to analyze the relationship between age group and reported driving after drinking.  


#1. Descriptive Statistics 

To start, we are going to compare our sample distribution overall with the `table1` package (version 1.5.1), comparing how our results change with and without weighting. We will apply weighting with the `survey` package (version 4.5). 

We are going to start with the overall distribution (though this will also be included in our (total) column later on once we stratify.) 

## 1.1 Overall Sample
### 1.1.1 Unweighted

```{r}

num_vars <- c(
  "family_home_risk_num",
  "physical_env_risk_num",
  "avg_pmk",
  "num_days_drink_02"
)

fac_vars <- c(
  "drive_after_drink", "sex",
  "ride_drink_2002", "age_group", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income"
) 

study_dat <- study_dat %>%
  mutate(across(all_of(fac_vars), as.factor))

table1(
  ~ family_home_risk_num +
    physical_env_risk_num +
    avg_pmk +
    num_days_drink_02 +
    drive_after_drink +
    sex +
    ride_drink_2002 +
    age_group +
    binge +
    marijuana +
    license +
    smoker +
    race_eth +
    mom_style +
    dad_style +
    education +
    income,
  data = study_dat
)
``` 

Next, we need to apply weighting to make this nationally representative. While we can use the `survey` package to achieve this in model fit, it becomes hard to do this for the table1 package we used before that gave us such nice output. 

###  1.1.2 Weighted 

We already specified our design in the loading chunk at the beginning. To fit the table and make this output look nicer, we will use `gtsummary`.

```{r overall_weighted}
vars <- c(
  num_vars,
  fac_vars
)

design_table_1 <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
)

tbl1_overall_weighted <- tbl_svysummary(
  design_table_1,
  include = c(
    all_of(num_vars),
    all_of(fac_vars)
  ),
   type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
)

tbl1_overall_weighted

```

## 1.2 Age-Group Stratified

Next, we want to stratify by our exposure, age_group, to check whether the distributions of all these variables differ by age at baseline.  

We are going to apply this to our weighted values only this time.  

### 1.2.1 Numeric Option

```{r stratified_weighted_table_1}

tbl1_weighted <- tbl_svysummary(
  design_table_1,
  by = age_group,
  include = c(all_of(num_vars), all_of(fac_vars)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_weighted
```

**Summary**

Among our significant results, we can see that individuals aged 21-24 have **higher** *average PMK*, *drink more number of days in 2002*, more reported *driving after drinking*, more reported *riding while drinking*, more *licensed*, more permissive *parenting styles*, higher *education*, and proportionally more in the $10k-$30k and $30k-$50k *income* brackets. 



### 1.1.2 Categorical Option 

We are going to do the same thing, this time replacing some of our variables with their categorical counterparts (family/home risk index, physical environment risk index, and parental monitoring knowledge).


```{r categorical_version_table_1} 
num_vars_v2 <- c(
  "num_days_drink_02"
)

fac_vars_cat <- c(
  "drive_after_drink", "sex",
  "ride_drink_2002", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income", "family_home_risk_cat", "physical_env_risk_cat",
  "avg_pmk_cat"
) 

tbl1_cat <- tbl_svysummary(
  design_table_1,
  by = age_group,
  include = c(all_of(num_vars_v2), all_of(fac_vars_cat)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_cat
```




Now we have a good idea about what variables might be associated with our exposure. We also can check what is associated with our outcome briefly to see if multiple variables are popping up, warranting their inclusion as covariates.  


## 1.3 Driving after Drinking Stratified 

### 1.3.1  Numeric option 

```{r outcome_stratified_numeric}

tbl1_w_outcome_numeric <- tbl_svysummary(
  design_table_1,
  by = drive_after_drink,
  include = c(all_of(num_vars), all_of(fac_vars)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_w_outcome_numeric 
```

### 1.3.2 Categorical option


```{r categorical_version_outcome} 
num_vars_v2 <- c(
  "num_days_drink_02"
)

fac_vars_cat <- c(
  "age_group", "sex",
  "ride_drink_2002", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income", "family_home_risk_cat", "physical_env_risk_cat",
  "avg_pmk_cat"
) 

tbl1_cat_outcome <- tbl_svysummary(
  design_table_1,
  by = drive_after_drink,
  include = c(all_of(num_vars_v2), all_of(fac_vars_cat)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_cat_outcome
```

