---
title: "03_Analysis"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide
---


```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)
library(haven) 
library(labelled) 
library(finalfit) 
library(naniar) 
library(purrr)
library(janitor)
library(skimr) 
library(survey) 
library(table1) 
library(tableone)
library(gtsummary) 
library(performance)


# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load data 
study_dat <- read.csv("../CleanData/study_dat.csv") 

# Variable Labels  

var_label(study_dat$id) <- "Respondent ID"

var_label(study_dat$stratum) <- "Sampling stratum"
var_label(study_dat$psu) <- "Primary sampling unit"
var_label(study_dat$weight) <- "Round 6 survey weight"

var_label(study_dat$age) <- "Age at Round 6 (2002)"
var_label(study_dat$age_group) <- "Age group"

var_label(study_dat$drive_after_drink) <- 
  "Drove after drinking alcohol in past 30 days"

var_label(study_dat$binge) <- 
  "Consumed 5+ drinks on one occasion in past 30 days"

var_label(study_dat$marijuana) <- 
  "Used marijuana in past 30 days"

var_label(study_dat$sex) <- "Biological sex"
var_label(study_dat$eth) <- "Ethnicity"
var_label(study_dat$race) <- "Race"
var_label(study_dat$race_eth) <- "Combined race/ethnicity"

var_label(study_dat$income) <- 
  "Annual household income (previous year)"

var_label(study_dat$education) <- 
  "Highest educational attainment"

var_label(study_dat$ride_drink_2002) <- 
  "Rode with drinking driver in 2002"

var_label(study_dat$family_home_risk_num) <- 
  "Family/home risk index (numeric)"

var_label(study_dat$family_home_risk_cat) <- 
  "Family/home risk index category"

var_label(study_dat$physical_env_risk_num) <- 
  "Physical environment risk index (numeric)"

var_label(study_dat$physical_env_risk_cat) <- 
  "Physical environment risk index category"

var_label(study_dat$substance_use_index_cat) <- 
  "Substance use index"

var_label(study_dat$num_cigs_02) <- 
  "Number of cigarettes smoked in past 30 days (2002)"

var_label(study_dat$age_first_drug_02) <- 
  "Age first used other drugs"

var_label(study_dat$baseline_mom_pmk) <- 
  "Baseline maternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_dad_pmk) <- 
  "Baseline paternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_mom_pmk_cat) <- 
  "Baseline maternal PMK category"

var_label(study_dat$baseline_dad_pmk_cat) <- 
  "Baseline paternal PMK category"

var_label(study_dat$avg_mom_pmk) <- 
  "Average maternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_dad_pmk) <- 
  "Average paternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_mom_pmk_cat) <- 
  "Average maternal PMK category"

var_label(study_dat$avg_dad_pmk_cat) <- 
  "Average paternal PMK category"

var_label(study_dat$license) <- 
  "Driver's License Status"  

var_label(study_dat$avg_pmk) <- 
  "Average PMK both Parents 1999-2000"

# Binary Variable Labels 

study_dat <- study_dat %>%
  mutate(

    drive_after_drink = factor(
      drive_after_drink,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    binge = factor(
      binge,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    marijuana = factor(
      marijuana,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ) , 
    
    sex = factor(
      sex, 
      levels = c(1,0), 
      labels = c("Male", "Female")
    ), 
    
    smoker = factor(
      smoker, 
      levels = c(0,1), 
      labels = c("No", "≥ 1 Cig in Last 30 Days")
    ), 

    license = factor(
      license, 
      levels = c(0,1), 
      labels = c("Unlicensed", "Licensed")
    ), 
    
   ride_drink_2002 =factor(
      ride_drink_2002, 
      levels = c(0,1), 
      labels = c("No", "Yes")
    )
    
  )

# More Factors 
study_dat <- study_dat %>%
  mutate(

    age_group = factor(
      age_group,
      levels = c("Pre-21", "21-24")
    ),

    income = factor(
      income,
      levels = c(
        "<=$10,000",
        "$10,001 - $30,000",
        "$30,001 - $50,000",
        "$50,001 - $80,000",
        ">$80,000"
      ),
      ordered = FALSE
    ),

    baseline_mom_pmk_cat = factor(
      baseline_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    baseline_dad_pmk_cat = factor(
      baseline_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    avg_mom_pmk_cat = factor(
      avg_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    avg_dad_pmk_cat = factor(
      avg_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    )
    
  )

#Changing reference level for race/eth 
study_dat$race_eth <- factor(study_dat$race_eth)

study_dat$race_eth <- relevel(
  study_dat$race_eth,
  ref = "Non-Black / Non-Hispanic"
)

design <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
) 
``` 

# Introduction 
 
 This script contains the code used to explore the NLSY97 data that was previously cleaned in the `"01_Cleaning.rmd"` file. The primary goals of this script are to: 

1. Generate **descriptive statistics** of the sample stratified by the exposure (age group), producing a table 1 with weighted (nationally representative) values

2. **Sequential logistic models** to analyze the relationship between age group and reported driving after drinking.  


#1. Descriptive Statistics 

To start, we are going to compare our sample distribution overall with the `table1` package (version 1.5.1), comparing how our results change with and without weighting. We will apply weighting with the `survey` package (version 4.5). 

We are going to start with the overall distribution (though this will also be included in our (total) column later on once we stratify.) 

## 1.1 Overall Sample
### 1.1.1 Unweighted

```{r}

num_vars <- c(
  "family_home_risk_num",
  "physical_env_risk_num",
  "avg_pmk",
  "num_days_drink_02"
)

fac_vars <- c(
  "drive_after_drink", "sex",
  "ride_drink_2002", "age_group", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income"
) 

study_dat <- study_dat %>%
  mutate(across(all_of(fac_vars), as.factor))

table1(
  ~ family_home_risk_num +
    physical_env_risk_num +
    avg_pmk +
    num_days_drink_02 +
    drive_after_drink +
    sex +
    ride_drink_2002 +
    age_group +
    binge +
    marijuana +
    license +
    smoker +
    race_eth +
    mom_style +
    dad_style +
    education +
    income,
  data = study_dat
)
``` 

Next, we need to apply weighting to make this nationally representative. While we can use the `survey` package to achieve this in model fit, it becomes hard to do this for the table1 package we used before that gave us such nice output. 

###  1.1.2 Weighted 

We already specified our design in the loading chunk at the beginning. To fit the table and make this output look nicer, we will use `gtsummary`.

```{r overall_weighted}
vars <- c(
  num_vars,
  fac_vars
)

design_table_1 <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
)

tbl1_overall_weighted <- tbl_svysummary(
  design_table_1,
  include = c(
    all_of(num_vars),
    all_of(fac_vars)
  ),
   type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
)

tbl1_overall_weighted

```

## 1.2 Age-Group Stratified

Next, we want to stratify by our exposure, age_group, to check whether the distributions of all these variables differ by age at baseline.  

We are going to apply this to our weighted values only this time.  

### 1.2.1 Numeric Option

```{r stratified_weighted_table_1}

tbl1_weighted <- tbl_svysummary(
  design_table_1,
  by = age_group,
  include = c(all_of(num_vars), all_of(fac_vars)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_weighted
```

#### Summary


Among our significant results, we can see that individuals aged 21-24 have **higher** *average PMK*, *drink more number of days in 2002*, more reported *driving after drinking*, more reported *riding while drinking*, more *licensed*, more permissive *parenting styles*, higher *education*, and proportionally more in the $10k-$30k and $30k-$50k *income* brackets. 



### 1.1.2 Categorical Option 

We are going to do the same thing, this time replacing some of our variables with their categorical counterparts (family/home risk index, physical environment risk index, and parental monitoring knowledge).


```{r categorical_version_table_1} 
num_vars_v2 <- c(
  "num_days_drink_02"
)

fac_vars_cat <- c(
  "drive_after_drink", "sex",
  "ride_drink_2002", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income", "family_home_risk_cat", "physical_env_risk_cat",
  "avg_pmk_cat"
) 

tbl1_cat <- tbl_svysummary(
  design_table_1,
  by = age_group,
  include = c(all_of(num_vars_v2), all_of(fac_vars_cat)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_cat
```

#### Summary of changes

This time, we see that the **family/home risk index category** is significantly different, with there appearing to be a larger proportion of under 21-year olds in the lowest category (0 to 399) and a slightly larger proportion in the highest category (700 to 999), while the 21-to-24-year-olds have greater proportions in the middle ranges (1000 to 1299 and 400 to 699). This does not give us a clear-cut interpretation or trend, however, and this index is therefore more likely to be an explanatory or mediating variable. It is not entirely clear here whether its inclusion in our model would improve it; it may be useful to explore this one in further detail later. 

Our **physical environment risk index category** did not pop up with any significant differences between groupings.  

**Average parental monitoring** did have significant differences, with a greater proportion of 21-to-24 year olds having the least amount of monitoring (0 to 4), and greater proportions of under 21-year olds having greater pmk. Something interesting though is the fact that this parental monitoring score is something that logically will be higher at baseline when participants are at their youngest. It makes its inclusion in this case tricky, as we do want to explore it as an explanatory factor in this relationship, but it may just be lower generally among our older participants who are also more likely to drink and drive... colinear? Mediating variable? We need to tease this one out further, and consider its inclusion in our models very carefully.



Now we have a good idea about what variables might be associated with our exposure. We also can check what is associated with our outcome briefly to see if multiple variables are popping up, warranting their inclusion as covariates.  


## 1.3 Driving after Drinking Stratified 

### 1.3.1  Numeric option 

```{r outcome_stratified_numeric}

tbl1_w_outcome_numeric <- tbl_svysummary(
  design_table_1,
  by = drive_after_drink,
  include = c(all_of(num_vars), all_of(fac_vars)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_w_outcome_numeric 
```

#### Summary  

Those who reported **drinking while driving** had *reduced* physical environment risk index, average parental monitoring, *greater* number of days drinking, more were male gender, more reported riding with someone while drinking, more were 21-24, more reported binge drinking, more marijuana use, more licensed, more Non-Black/Non-Hispanic (and less Black and Hispanic), no difference of parenting styles, less likely to have higher education, and a greater proportion with >80k household income.


### 1.3.2 Categorical option


```{r categorical_version_outcome} 
num_vars_v2 <- c(
  "num_days_drink_02"
)

fac_vars_cat <- c(
  "age_group", "sex",
  "ride_drink_2002", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income", "family_home_risk_cat", "physical_env_risk_cat",
  "avg_pmk_cat"
) 

tbl1_cat_outcome <- tbl_svysummary(
  design_table_1,
  by = drive_after_drink,
  include = c(all_of(num_vars_v2), all_of(fac_vars_cat)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_cat_outcome
```


#### Summary 

This time, family/home index is insignificant, a greater proportion of those who drove after drinking had a lower physical environment risk index, and those who drove after drinking had a greater proportion for parental monitoring among categories of 0 to 4 and 5 to 8 (lowest and second highest).  


#2. Sequential Models 

We are going to explore our sequential survey-weighted models, exploring how different variables interact in this causal framework.  

We will be using logistic regression to estimate how the odds of driving after drinking change depending on age group and other covariates. 


## 2.1 Crude Model   

We also need to make an important distinction: will we use a binomial family (logistic regression), or will we use a quasibinomial family? We would opt for the quasibinomial if we had overdispersion in our outcome.

```{r 2.1}   
mod1 <- svyglm(
  drive_after_drink ~ age_group,
  design = design,
  family = binomial()
) 

summary(mod1) 
summary(mod1)$dispersion 

tidy(mod1, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)

```

We have a dispersion parameter of about 1, suggesting no evidence of overdispersion, so we are good to continue with a binomial family in our future set of models.  

**Model Interpretation** 

In the survey-weighted unadjusted logistic regression model, individuals aged 21-24 years old had significantly higher odds (OR = 2.5, 95% CI: 2.13, 3.02 , p < .001) of reporting driving after drinking compared with individuals >21 years.  

## 2.2 Demographics

Next, we are going to add some demographic characteristics. We are going to start with sex and race/ethnicity.

```{r 2.2}
mod2 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth,
  design = design,
  family = binomial()
) 

tidy(mod2, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 

**Model Interpretation**   

After adjusting for sex and race/ethnicity, individuals aged 21-24 had 2.56x the odds of reporting driving after drinking (95% CI: 2.15 to 3.05). 

Looking at individual estimates, females had reduced odds of driving after drinking, while Hispanics, Mixed Race (Non-Hispanic), and Non-Black/Non-Hispanic had increased odds relative to Blacks -- need to change the reference category for this one. Let's keep trekking on while we figure out what we want to do.

## 2.3 Adding Risk/Socioeconomic Contexts

Next, we are going to add the family and physical environment risk contexts. We are going to start with the numeric versions.

```{r 2.3}
mod3 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  family_home_risk_num +
  physical_env_risk_num,
  design = design,
  family = binomial()
) 

tidy(mod3, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 

**Model Interpretation** 

This time, our Odds Ratio for 21-24 year olds changed quite a bit, from ~2.5 to 3.54. This could indicate that the family/home risk and physical/environment risk were confounding the relationship potentially, or that something else is going on... must remember that these two variables had a lot of missingness, and they are also popping up as being statistically significant despite having null effect estimates.... But these are also on the numeric scale. We could consider putting the categorical version in instead to see what pops up? But also, ultimately, they may not be as important for our context... colinear with household income perhaps?? Let's return to this.   

We are going to this time just add family and environmental separately as categorical indexes. 

```{r}
#family 
fam_mod <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  family_home_risk_cat ,
  design = design,
  family = binomial()
)  
tidy(fam_mod, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
#environmental 
env_mod <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  physical_env_risk_cat,
  design = design,
  family = binomial()
)  

tidy(env_mod, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 
For family risk,  the OR for age group went wayyy up for nearly everything? There are no groups with reduced risk in this model. This to me looks extremely unstable, probably due to our missing data.  

The environmental predictor had much more believable estimates, though physical env wasn't a significant predictor at any level. The only significant predictors here were age group, sex, Black race, and Hispanic race. The issue, however, is that env is likely pretty intrinsically involved in income, and to a certain extent other demographic indicators as well... we likely need to select one or the other. I'd lean much more towards income due to its having more complete data.

Let's check out household income briefly next: 

```{r 2.3.2}
mod3.2 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + income,
  design = design,
  family = binomial()
) 

tidy(mod3.2, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 
If we hold everything constant and just look at the income levels, it looks like we only have significance for the group that is over $80k (compared to >10k?) with having increased odds of driving after drinking. We also changed this over from an ordered factor for ease of interpretation, but this should in theory just take care of some of the socioeconomic differences. 

Let's compare the models using an ANOVA to see whether income helps explain more of the variation here: 

```{r} 

anova_income <- anova(mod2, #race and sex 
                      mod3.2 #with income
                      ) 

print(anova_income)
``` 
With our anova, we tested whether the inclusion of income adds explanatory power for drive_after_drink after adjusting for other covariates. Our test statistic is 7.28, with a p-value of 0.1226. 

Based on this, the addition of income to the model didn't meaningfully improve our prediction of driving after drinking after accounting for age, sex, and race/ethnicity. 

I am also curious whether the environmental index is a preferable predictor, in this case. Let's try comparing the two, looking both categorically and numerically: 

```{r}  
#Categorical
mod_env1 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  physical_env_risk_cat,
  design = design,
  family = binomial()
)  

summary(mod_env1)

anova_env1 <- anova(mod2, #race and sex 
                      mod_env1 #with env, cat
                      ) 

print(anova_env1) 

#Numerically 
mod_env2 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  physical_env_risk_num,
  design = design,
  family = binomial()
)  

summary(mod_env2)

anova_env2 <- anova(mod2, #race and sex 
                      mod_env2 #with env, numeric
                      ) 

print(anova_env2)
```
Interestingly, while it appears that the numeric version makes more sense intuitively in our model results, its addition doesn't add much in terms of predictivity in our model output. 

## 2.4 Parental Monitoring 

```{r 2.4}
mod4 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth +
  family_home_risk_num +
  physical_env_risk_num + avg_pmk,
  design = design,
  family = binomial()
) 

tidy(mod4, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 

**Model Interpretation**   

Our age group term also changed a bit from before, jumping up from 2.5 to 3.3 after controlling for all these things. But I am still skeptical when we include the risk categories numerically. 

Let's try again, this time exclusing the risk indicators. 

```{r 2.4.2}
mod4.2 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + avg_pmk,
  design = design,
  family = binomial()
) 

tidy(mod4.2, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value) 

mod4.3 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + avg_pmk_cat,
  design = design,
  family = binomial()
) 

tidy(mod4.3, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value) 

``` 

**Model Interpretation**   
This looks a lot more realistic, our odds ratio for 21-24 is a lot closer to where it was before, though it did still increase slightly. This time, it appears that each unit increase in PMK is associated with a 10% reduction in the odds of reporting driving while drinking, controlling for age, sex, and race/eth. On the other hand, being 21-24 is associated with 2.6x greater odds of driving after drinking, controlling for sex, race, and parental monitoring knowledge. 

This would be a very intriguing interaction... Let's check it out!

## 2.5 Interaction Testing 

We are going to test a series of models here, this time examining whether our observed effects differ when introducing interaction terms. We are just going to include the interaction terms alone here before introducing them back into the full model, just to see what we can observe.

```{r 2.5}
#PMK 
mod_pmk <- svyglm(
  drive_after_drink ~ age_group*avg_pmk,
  design = design,
  family = binomial()
)

#Sex 
mod_sex <-  svyglm(
  drive_after_drink ~ age_group*sex,
  design = design,
  family = binomial()
)  

#Race 
 mod_race <- svyglm(
  drive_after_drink ~ age_group*race_eth, 
  design = design,
  family = binomial()
)  
 
  
#Binge 
 mod_binge <-   svyglm(
  drive_after_drink ~ age_group*binge,
  design = design,
  family = binomial()
)  
 
#Income 
 mod_income <- svyglm(
  drive_after_drink ~ age_group*income,
  design = design,
  family = binomial()
)  

 regTermTest(mod_race, ~ age_group:race_eth)
regTermTest(mod_sex, ~ age_group:sex)
regTermTest(mod_binge, ~ age_group:binge) 
 regTermTest(mod_pmk, ~ age_group:avg_pmk) 
  regTermTest(mod_income, ~ age_group:income)
``` 
**Interaction Summaries**

It appears that there is a possible interaction effect for parental monitoring knowledge only. 


Another consideration: we have a ton of missingness for marijuana, smoker, PMK, family risk, and physical environment, making their inclusion in these models also needing to be carefully considered.  

Potential framework: 
Mod 1: age (crude) 
Mod 2: age sex race/eth (income??)
Mod 3: Mod 2 + PMK (with interaction?), evaluate other variables 


### Proposed sequential framework 
Here is the output following the proposed framework:  

```{r}
#Mod 1 (Crude)
tidy(mod1, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value) 

#Mod 2 (Demographics)  
mod2.1 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + income,
  design = design,
  family = binomial()
) 

tidy(mod2.1, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)

#Mod 3 (Evaluate other variables) 

mod3.3 <- svyglm(
  drive_after_drink ~ age_group*avg_pmk + sex + race_eth + income,
  design = design,
  family = binomial()
)  
tidy(mod3.3, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)

```

