---
title: "04_Final_Analysis"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float: true
    code_folding: hide
---


```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(ggplot2) 
library(readxl) 
library(lubridate)
library(broom)
library(viridis)
library(haven) 
library(labelled) 
library(finalfit) 
library(naniar) 
library(purrr)
library(janitor)
library(skimr) 
library(survey) 
library(table1) 
library(tableone)
library(gtsummary) 
library(performance)


# Global options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load data 
study_dat <- read.csv("../CleanData/study_dat.csv") 

# Variable Labels  

var_label(study_dat$id) <- "Respondent ID"

var_label(study_dat$stratum) <- "Sampling stratum"
var_label(study_dat$psu) <- "Primary sampling unit"
var_label(study_dat$weight) <- "Round 6 survey weight"

var_label(study_dat$age) <- "Age at Round 6 (2002)"
var_label(study_dat$age_group) <- "Age group"

var_label(study_dat$drive_after_drink) <- 
  "Drove after drinking alcohol in past 30 days"

var_label(study_dat$binge) <- 
  "Consumed 5+ drinks on one occasion in past 30 days"

var_label(study_dat$marijuana) <- 
  "Used marijuana in past 30 days"

var_label(study_dat$sex) <- "Biological sex"
var_label(study_dat$eth) <- "Ethnicity"
var_label(study_dat$race) <- "Race"
var_label(study_dat$race_eth) <- "Combined race/ethnicity"

var_label(study_dat$income) <- 
  "Annual household income (previous year)"

var_label(study_dat$education) <- 
  "Highest educational attainment"

var_label(study_dat$ride_drink_2002) <- 
  "Rode with drinking driver in 2002"

var_label(study_dat$family_home_risk_num) <- 
  "Family/home risk index (numeric)"

var_label(study_dat$family_home_risk_cat) <- 
  "Family/home risk index category"

var_label(study_dat$physical_env_risk_num) <- 
  "Physical environment risk index (numeric)"

var_label(study_dat$physical_env_risk_cat) <- 
  "Physical environment risk index category"

var_label(study_dat$substance_use_index_cat) <- 
  "Substance use index"

var_label(study_dat$num_cigs_02) <- 
  "Number of cigarettes smoked in past 30 days (2002)"

var_label(study_dat$age_first_drug_02) <- 
  "Age first used other drugs"

var_label(study_dat$baseline_mom_pmk) <- 
  "Baseline maternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_dad_pmk) <- 
  "Baseline paternal parental monitoring knowledge score (1997)"

var_label(study_dat$baseline_mom_pmk_cat) <- 
  "Baseline maternal PMK category"

var_label(study_dat$baseline_dad_pmk_cat) <- 
  "Baseline paternal PMK category"

var_label(study_dat$avg_mom_pmk) <- 
  "Average maternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_dad_pmk) <- 
  "Average paternal parental monitoring knowledge score (1997-2000)"

var_label(study_dat$avg_mom_pmk_cat) <- 
  "Average maternal PMK category"

var_label(study_dat$avg_dad_pmk_cat) <- 
  "Average paternal PMK category"

var_label(study_dat$license) <- 
  "Driver's License Status"  

var_label(study_dat$avg_pmk) <- 
  "Average PMK both Parents 1999-2000"

# Binary Variable Labels 

study_dat <- study_dat %>%
  mutate(

    drive_after_drink = factor(
      drive_after_drink,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    binge = factor(
      binge,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ),

    marijuana = factor(
      marijuana,
      levels = c(0,1),
      labels = c(
        "No",
        "Yes"
      )
    ) , 
    
    sex = factor(
      sex, 
      levels = c(1,0), 
      labels = c("Male", "Female")
    ), 
    
    smoker = factor(
      smoker, 
      levels = c(0,1), 
      labels = c("No", "≥ 1 Cig in Last 30 Days")
    ), 

    license = factor(
      license, 
      levels = c(0,1), 
      labels = c("Unlicensed", "Licensed")
    ), 
    
   ride_drink_2002 =factor(
      ride_drink_2002, 
      levels = c(0,1), 
      labels = c("No", "Yes")
    )
    
  )

# More Factors 
study_dat <- study_dat %>%
  mutate(

    age_group = factor(
      age_group,
      levels = c("Pre-21", "21-24")
    ),

    income = factor(
      income,
      levels = c(
        "<=$10,000",
        "$10,001 - $30,000",
        "$30,001 - $50,000",
        "$50,001 - $80,000",
        ">$80,000"
      ),
      ordered = FALSE
    ),

    baseline_mom_pmk_cat = factor(
      baseline_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    baseline_dad_pmk_cat = factor(
      baseline_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    avg_mom_pmk_cat = factor(
      avg_mom_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    ),

    avg_dad_pmk_cat = factor(
      avg_dad_pmk_cat,
      levels = c(
        "0 TO 4",
        "5 TO 8",
        "9 TO 12",
        "13 TO 16"
      ),
      ordered = FALSE
    )
    
  )

#Changing reference level for race/eth 
study_dat$race_eth <- factor(study_dat$race_eth)

study_dat$race_eth <- relevel(
  study_dat$race_eth,
  ref = "Non-Black / Non-Hispanic"
)

design <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
) 
``` 

# Introduction 
 
 This script contains the final output for the final analyses conducted for aim 1. 

We will begin with descriptive statistics for our table 1, then our series of sequential models. 

# Table 1  

```{r}
design_table_1 <- svydesign(
  ids = ~id,
  weights = ~weight,
  data = study_dat
)

num_vars_v2 <- c(
  "num_days_drink_02"
)

fac_vars_cat <- c(
  "drive_after_drink", "sex",
  "ride_drink_2002", "binge", "marijuana",
  "license", "smoker", "race_eth", "mom_style",
  "dad_style", "education", "income", "family_home_risk_cat", "physical_env_risk_cat",
  "avg_pmk_cat"
) 

tbl1_cat <- tbl_svysummary(
  design_table_1,
  by = age_group,
  include = c(all_of(num_vars_v2), all_of(fac_vars_cat)),
  type = list(
    binge ~ "categorical",
    marijuana ~ "categorical",
    ride_drink_2002 ~ "categorical"
  ),
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_p() 

tbl1_cat
```

# Sequential Models 

## Model 1: Crude Model 

```{r}
mod1 <- svyglm(
  drive_after_drink ~ age_group,
  design = design,
  family = binomial()
) 

summary(mod1) 
summary(mod1)$dispersion 

tidy(mod1, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)

```

**Model Interpretation** 

In the survey-weighted unadjusted logistic regression model, individuals aged 21-24 years old had significantly higher odds (OR = 2.5, 95% CI: 2.13, 3.02 , p < .001) of reporting driving after drinking compared with individuals >21 years.

## Model 2: Demographics   

Next, we are going to add some demographic characteristics. We are going to start with sex, race/ethnicity, and income.

```{r}
mod2 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + income,
  design = design,
  family = binomial()
) 

tidy(mod2, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value)
``` 

**Model Interpretation**   

[UPDATE]
After adjusting for sex and race/ethnicity, individuals aged 21-24 had 2.56x the odds of reporting driving after drinking (95% CI: 2.15 to 3.05). 

Looking at individual estimates, females had reduced odds of driving after drinking, while Hispanics, Mixed Race (Non-Hispanic), and Non-Black/Non-Hispanic had increased odds relative to Blacks -- need to change the reference category for this one. Let's keep trekking on while we figure out what we want to do.


## Model 3: Risk Factors  

Next, we are going to add some risk/protective factors around driving and drinking, paying special attention to the variables that popped as having a statistically significant association with our exposure. While education pops up, we will not be including it due to its colinearity with income. 

```{r}
mod_3 <- svyglm(
  drive_after_drink ~ age_group + sex + race_eth + income + 
     num_days_drink_02 + ride_drink_2002  + license +
    family_home_risk_cat,
  design = design,
  family = binomial()
) 

tidy(mod_3, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value) 
```

## Model 4: Parental Monitoring Knowledge

```{r}
mod_4 <- svyglm(
  drive_after_drink ~ age_group*avg_pmk_cat + sex + race_eth + income + 
     num_days_drink_02 + ride_drink_2002 + education + license +
    family_home_risk_cat,
  design = design,
  family = binomial()
) 

tidy(mod_4, conf.int = TRUE) %>%
  mutate(
    OR = exp(estimate),
    CI_low = exp(conf.low),
    CI_high = exp(conf.high)
  ) %>%
  select(term, OR, CI_low, CI_high, p.value) 
```

